---
title: "Crab feeding behavior"
author: "Julianna Renzi"
date: "4/21/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(here)
require(tidyverse)
require(RColorBrewer)
require(FSA) # for dunn test
```

# Bring in the data

```{r}
# bring in the csv that has the percent cover of each nubbin, determined beforehand using ImageJ
perCover <- read_csv(here("data/ImageJ_crab_feeding.csv"))

# bring in the bite count data from the videos
behavior <- read_csv(here("data/Crab_feed_behavior.csv"))
```

# Calculate Strauss' index to assess preference

Join the dataframes by the trial number and add derived columns (e.g., total number of bites, percent cover, Strauss' index, etc.). Strauss' linear selectivity index was taken from the Transactions of the American Fisheries Society, 1979 ("Reliability estimates fro Ivlev's electivity index, the forage ratio, and a proposed linear index of food selection") and is just the difference in the proportion of bites taken vs. the availability of the resource. That means that the index ranges from -1 to 1, with positive values indicating a preference, negative values indicating avoidance, and 0 indicating no preference. It also means that t-statistics can be used for statistical comparison, according to Strauss.

```{r}
behavior %>% 
  full_join(perCover, by = "Trial") %>% 
  
  # add columns for percent cover
  mutate(Total_pixels = Alive_Pixels + Margin_Pixels + Dead_Pixels + Turf_Pixels + BrokenOff_Pixels,
         Prop_dead = Dead_Pixels / Total_pixels,
         Prop_margin = Margin_Pixels / Total_pixels,
         Prop_alive = Alive_Pixels / Total_pixels) %>% 
  
  # add columns for percent of bites
  mutate(Total_bites = Bites_alive + Bites_margin + Bites_dead,
         Prop_bites_dead = Bites_dead / Total_bites,
         Prop_bites_margin = Bites_margin / Total_bites,
         Prop_bites_alive = Bites_alive / Total_bites) %>% 
  
  # calculate the indecies
  mutate(Dead = Prop_bites_dead - Prop_dead,
         Margin = Prop_bites_margin - Prop_margin,
         Alive = Prop_bites_alive - Prop_alive) %>% 
  
  # remove the crabs that did not feed
  filter(Total_bites != 0) -> strauss
```

Also do a reformatted version that might be easier for some tasks

```{r}
strauss %>% 
  # reformat so it's easier to plot
  pivot_longer(cols = c(Dead, Margin, Alive), names_to = "Substrate", values_to = "Preference") -> strauss_long
```


# Calculate statistics

Are these values different than zero?

```{r}
t.test(strauss$Dead, mu = 0) # is different
t.test(strauss$Margin, mu = 0) # is different
t.test(strauss$Alive, mu = 0) # is different

# these are signifiant even with a Bonferonni correction for doing 3 separate tests:
0.05/3
```

Are these values different from each other? 

```{r}
kruskal.test(Preference ~ Substrate, data = strauss_long) # this is non-parametric

m1 <- aov(Preference ~ Substrate, data = strauss_long) # this is parametric
  summary(m1) # they are different either way


dunnTest(Preference ~ as.factor(Substrate),
         data = strauss_long,
         method="bonferroni")
```



# Plot results

```{r}
# want to order it as alive, margin, dead for aesthetics
level_order <- c('Alive', 'Margin', 'Dead') 

# pdf(here("figures/feeding_pref.pdf"), width = 6, height = 4)
strauss_long %>% 
  # plot
  ggplot(aes(x = factor(Substrate, level = level_order), y = Preference, fill = Substrate)) +
  geom_boxplot() +
  labs(x = "Substrate", y = "Preference") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  scale_fill_brewer(palette="Oranges") + 
  geom_point(alpha = 0.5) +
  theme_classic() +
  theme(text = element_text(size=15), legend.position="none") +
  xlab("") +
  ylim(-1, 1) +
  stat_summary(geom = 'text', label = c("a", "b", "c"), fun.y = max, vjust = -1, size=6, color = c("black", "black", "black")) # add letters for significance

# dev.off()

```





