---
title: "Field data explore"
author: "Julianna Renzi"
date: "3/3/2023"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(tidyverse)
require(here)
require(nlme)
```

# Read in algae data

```{r}
algae <- read_csv(here("data/field_experiment/algae_weight.csv"))

size <- read_csv(here("data/field_experiment/colony_specs.csv"))

monitoring <- read_csv(here("data/field_experiment/colony_monitoring.csv"))
```

# Make sure initial treatments were the same

```{r}
algae %>% 
  select(NW_algae_initial_weight, W_algae_intial_weight, Colony_ID) %>% 
  pivot_longer(cols = c(NW_algae_initial_weight, W_algae_intial_weight),
               names_to = "Treatment", 
               values_to = "Biomass") -> init_biomass

```

Plot

```{r}
init_biomass %>% 
  ggplot(aes(x = Treatment, y = Biomass, fill = Treatment)) +
  geom_boxplot() +
  ylab("Initial biomass (g)") +
  scale_fill_brewer(palette="Oranges") + 
  geom_point(alpha = 0.5) +
  theme_classic() +
  theme(text = element_text(size=18), legend.position="none") +
  xlab("") +
  # rename categories
  scale_x_discrete(labels = c('No wounding','Wounding'))

```

Looks like wounding is a little higher. Check to see if this is a significant difference:

```{r}
init.M <- aov(Biomass ~ Treatment, data = init_biomass)
  summary(init.M) # looks okay
```

Although they're not different, probably makes sense to do % biomass loss


# Look at percent change

```{r}
algae %>% 
  mutate(NW_change = NW_algae_initial_weight - NW_final_weight,
         W_change = W_algae_intial_weight - W_final_weight) %>%
  mutate(NW_perc_change = NW_change/NW_algae_initial_weight,
         W_perc_change = W_change/W_algae_intial_weight) %>%
  select(Colony_ID, NW_perc_change, W_perc_change) %>% 
  pivot_longer(cols = c(NW_perc_change, W_perc_change),
               names_to = "Treatment", 
               values_to = "Percent_change") -> perc_change
```

## Plot percent

```{r}
perc_change %>% 
  ggplot(aes(x = Treatment, y = Percent_change)) +
  geom_boxplot() +
  ylab("Biomass loss (%)") +
  theme_bw()
```

```{r}
perc_change %>% 
  mutate(Percent_change = 100*Percent_change) %>% 
  ggplot(aes(x = Treatment, y = Percent_change, fill = Treatment)) +
  geom_boxplot() +
  ylab("Biomass loss (%)") +
  scale_fill_brewer(palette="Oranges") + 
  geom_point(alpha = 0.5) +
  theme_classic() +
  theme(text = element_text(size=18), legend.position="none") +
  xlab("") +
  # rename categories
  scale_x_discrete(labels = c('No wounding','Wounding'))

ggsave(here("figures/field_algal_loss.jpg"), height = 4, width = 6)

```





## Percent stats

Want a random effect for Coral colony, since we use a paired design with 1 patch of each treatment/coral. Helps account for flow, etc.

```{r}
m.PercRE <- lme(Percent_change~Treatment, 
                random=~1|Colony_ID, 
                data=perc_change)
  anova(m.PercRE) # Cool! 

  
```

# Look at total change

This is not presented in the paper, but useful to check that they show the same effect

```{r}
algae %>% 
  mutate(NW_change = NW_algae_initial_weight - NW_final_weight,
         W_change = W_algae_intial_weight - W_final_weight) %>%
  select(Colony_ID, NW_change, W_change) %>% 
  pivot_longer(cols = c(NW_change, W_change),
               names_to = "Treatment", 
               values_to = "Biomass_change") -> biom_change
```

## Plot total loss

```{r}
biom_change %>% 
  ggplot(aes(x = Treatment, y = Biomass_change)) +
  geom_boxplot() +
  ylab("Biomass loss (g)") +
  theme_bw()
```


## Total loss stats

```{r}
# with random effect
m.BiomRE <- lme(Biomass_change~Treatment, 
                random=~1|Colony_ID, 
                data=biom_change)
  anova(m.BiomRE) # Cool! 
```



