---
title: "Map of Heron Island"
author: "Julianna Renzi"
date: "11/10/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(tidyverse) # data wrangling
require(here) # relative paths
require(sf) # for shape files
require(wesanderson) # for colors

```

# Bring in the data

This data comes from Great Barrier Reef Marine Park Authority 2014. Because the files are larger, we store them outside of the project in a folder called "GBRMPA_ship". To download them go to the Great Barrier Reef Marine Park Authority's data portal: http://www.gbrmpa.gov.au/geoportal/catalog/download/download.page 

```{r}
# Use this run-around method to go up a directory
setwd(here())
  setwd('..') # up one level
    wd.tmp <- getwd()

# Great Barrier Reef features
gbrFeatures <- read_sf(paste(wd.tmp, "GBRMPA_shp", "Great_Barrier_Reef_Features.shp", sep = "/"))

# GBR marine park zoning
gbrMPZ <- read_sf(paste(wd.tmp, "GBRMPA_shp", "Great_Barrier_Reef_Marine_Park_Zoning.shp", sep = "/"))


```

Check coordinate reference system

```{r}
st_crs(gbrFeatures) # see they're in GDA94 
```

Create our color palette from the Wes Anderson package

```{r}
vibRed <- wes_palette("Darjeeling1", n = 5)[1]
forGreen <- wes_palette("Darjeeling1", n = 5)[2]
lightO <- wes_palette("Darjeeling1", n = 5)[3]
darkO <- wes_palette("Darjeeling1", n = 5)[4]
skyB <- wes_palette("Darjeeling1", n = 5)[5]

```


Plot the Great Barrier Reef as a whole and the position of Heron Island on the Reef

```{r}
# get Heron Island boundaries as a bounding box
HI_bb <- st_as_sfc(st_bbox(gbrFeatures[gbrFeatures$GBR_NAME == "Heron Reef", ]))


# plot GBR and highlight the location of Heron
gbrFeatures %>% 
  ggplot() +
    geom_sf(data = gbrFeatures, fill = lightO) +
    theme_minimal() +
    # geom_text(aes(x = 145, y = -25, label = "Australia")) +
  geom_sf(data = HI_bb, fill = NA, color = skyB, size = 3) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) -> GBRfig

# ggsave(here("figures", "australiamap.pdf"), GBRfig, width = 5, height = 5)
```

Zoom in on Heron Island

```{r}
# first get the zones on Heron Reef
HIzone <- st_intersection(gbrMPZ, HI_bb)

# then subset our map to just include the scientific research zone and marine national park zone (two adjacent to Heron Island)
HI_SciMPA <- st_as_sfc(st_bbox(
  HIzone[(HIzone$LOC_NAME_S == "Scientific Research Zone" | HIzone$LOC_NAME_S == "Marine National Park Zone" ), ])
  )

# subset zoning based on this
HIzone <- st_intersection(gbrMPZ, HI_SciMPA)

# subset features based on this
HIfeat <- st_intersection(gbrFeatures, HI_SciMPA)


# plot zoomed in area
ggplot() +
  geom_sf(data = HIfeat, aes(fill = GBR_NAME), alpha = 0.5) +
  scale_fill_manual(name = "Feature", values = c("black", lightO, skyB,
                                                 NA, "lightgray", forGreen)) +
  geom_sf(data = HIzone, aes(fill = LOC_NAME_S), alpha = 0.5, color = darkO) +
  theme_void() +
  geom_text(aes(label = c("Heron Reef", "Wistari Reef"), 
                x = c(151.94, 151.90), 
                y = c(-23.45, -23.47))) +
  theme(legend.position = "top") -> HIfig


# ggsave(here("figures", "heronIslandmap.pdf"), HIfig, width = 5, height = 5)

```



Do: subset just the national park and scientific research zone, add scale bar + north arrow, fix color scheme to match


