---
title: "Survival analysis"
author: "Julianna Renzi"
date: "11/9/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(tidyverse) # data manipulation
require(here) # relative file paths
require(lubridate) # dates and times
require(wesanderson) # color palette
require(patchwork) # combining figures
require(survival) # surviavl analysis
require(survminer) # plotting survival curves
```

# Bring in the data

```{r}
# CSV with the day each coral "died"/was pulled from the experiment
# corals had a censored value of "0" if they either (1) made it to the end of the experiment without "dying" or (2) were dropped/broke (corals 7 and 29)
deathDat <- read_csv(here("data/Coral_survival.csv"))

```
# Prepare the data

```{r}
# calculate number of days to death (this is easy because the experiment started at the beginning of the month)
deathDat %>% 
  mutate(Death_day = as.character(Death_day)) %>% 
  rowwise %>% 
  mutate(Delta_time = str_split(Death_day, "/")[[1]][2]) %>% 
  mutate(Delta_time = as.numeric(Delta_time)) -> surv_df
```


Create our color palette from the Wes Anderson package

```{r}
vibRed <- wes_palette("Darjeeling1", n = 5)[1]
forGreen <- wes_palette("Darjeeling1", n = 5)[2]
lightO <- wes_palette("Darjeeling1", n = 5)[3]
darkO <- wes_palette("Darjeeling1", n = 5)[4]
skyB <- wes_palette("Darjeeling1", n = 5)[5]

```

# Plot the survival among treatments

```{r}
# order the treatments
surv_df$Treatment <- factor(surv_df$Treatment,levels = c("NAN", "NAW",  
                                                         "NNW", "NNN", "CAN",
                                                         "CAW", "CNN", "CNW"))

# broken up by no wounding:
surv_df %>% 
  filter(Coral_ID != 7, Coral_ID != 29) %>% # get rid of the ones that were dropped 
  filter(Treatment == "NAN" | Treatment == "NNN" | Treatment == "CAN" | Treatment == "CNN") %>% 
  ggplot(aes(x = Treatment, y = Delta_time, fill = Algae_treatment)) +
  geom_boxplot(size = 1) +
  scale_fill_manual(values = alpha(c(darkO, forGreen), 0.7)) +
  ylab("Number of days to death") +
  ggtitle("No wounding") +
  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25)) +
  theme_classic() +
  theme(text = element_text(size = 20), legend.position = "none",
        axis.title.x=element_blank(),
        axis.text.x=element_blank(), 
        axis.ticks.x=element_blank()) -> boxp.nowound


# and wounding:
surv_df %>% 
  filter(Coral_ID != 7, Coral_ID != 29) %>% # get rid of the dropped ones
  filter(Treatment == "NAW" | Treatment == "NNW" | Treatment == "CAW" | Treatment == "CNW") %>% 
  ggplot(aes(x = Treatment, y = Delta_time, fill = Algae_treatment)) +
  geom_boxplot(size = 1) +
  scale_fill_manual(values = alpha(c(darkO, forGreen), 0.7)) +
  ylab("Number of days to death") +
  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25)) +
  ggtitle("Wounding") +
  scale_x_discrete(labels=c("Algae","Control","Crab + Algae","Crab")) +
  theme_classic() +
  theme(text = element_text(size = 20), legend.position = "none") -> boxp.wound

```

Plot them together

```{r}
# pdf(here("figures/surivalBoxplts.pdf"), height = 9, width = 7.5)

boxp.nowound / boxp.wound

# dev.off()
```

# Survival analysis

First create a survival object using the Kaplan-Meier method. The Kaplan-Meier estimator is a non-parametric (survival data are skewed) statistic that allows us to estimate the survival function. At t = 0 the Kaplan-Meier estimate is 1 and with t -> inf the estimator approaches 0 (no survival). It assumes that the probability of surviving past a certain time point t is equal to the product of the observed survival rates until time point t and that proportions are conditional on the previous proportions (only take into account those that survived previous t). For this we want to order survival times in order of increasing duration first, then calculate S(t) (the survival probability at time t) by multiplying surviving proportions in each step. The `survival` package does this for us. Ref: https://www.datacamp.com/community/tutorials/survival-analysis-R and http://www.sthda.com/english/wiki/cox-proportional-hazards-model

```{r}
surv_object <- Surv(time = surv_df$Delta_time, # time to death
                    event = surv_df$Censored) # Censored points: 0 = right censored (not a true death), 1 = event at time
  
```

Create a full cox proportional hazards regression model. Note that a hazard ratio (HR) > 1 is an increased risk of death and HR < 1 is a decreased risk.

```{r}
full.coxph <- coxph(surv_object ~ Crab_treatment * Algae_treatment * Wounding_treatment, 
                    data = surv_df) # note response here must be a survival object returned by the Surv funtion (why we make the surv_object above)

```

## Model selection

Now we want to winnow down the terms

```{r}
coxph.1 <- coxph(surv_object ~ Crab_treatment + Algae_treatment + Wounding_treatment +
                   Crab_treatment:Algae_treatment +
                   Crab_treatment:Wounding_treatment +
                   Algae_treatment:Wounding_treatment,
                 data = surv_df)

anova(full.coxph, coxph.1, test = 'Chisq') # no difference
```

```{r}
# drop the least significant highest order term
coxph.2 <- coxph(surv_object ~ Crab_treatment + Algae_treatment + Wounding_treatment +
                   Crab_treatment:Wounding_treatment +
                   Algae_treatment:Wounding_treatment,
                 data = surv_df)

anova(coxph.1, coxph.2, test = 'Chisq') # looks okay--continue reducing
```

```{r}
# drop the least significant highest order term
coxph.3 <- coxph(surv_object ~ Crab_treatment + Algae_treatment + Wounding_treatment +
                   Crab_treatment:Wounding_treatment,
                 data = surv_df)

anova(coxph.2, coxph.3, test = 'Chisq') # looks okay--continue reducing
```

```{r}
# drop the highest order term
coxph.4 <- coxph(surv_object ~ Crab_treatment + Algae_treatment + Wounding_treatment,
                 data = surv_df)

anova(coxph.3, coxph.4, test = 'Chisq') # looks like we took it one step too far
```

```{r}
# check to make sure this simpler model isn't better
coxph.5 <- coxph(surv_object ~ Crab_treatment + Algae_treatment,
                 data = surv_df)


AIC(full.coxph, coxph.1, coxph.2, coxph.3, coxph.4, coxph.5) # Nope, looks like the best model is Model 3


# set it as our model
mCox <- coxph.3
  summary(mCox) # see the model overall is also significant (Wald test, LRT, longrank)

```

## Plot hazards model

Plot survival curves as a function of the different treatments

```{r}
# first for JUST crabs:
crab_df <- with(surv_df,
               data.frame(Crab_treatment = c("Y", "N"), 
                          Algae_treatment = c("N", "N"),
                          Wounding_treatment = c("N", "N")))
  
c.fit <- survfit(mCox, newdata = crab_df, data = surv_df)

# for JUST algae:
alg_df <- with(surv_df,
                data.frame(Crab_treatment = c("N", "N"), 
                           Algae_treatment = c("Y", "N"),
                           Wounding_treatment = c("N", "N")))

a.fit <- survfit(mCox, newdata = alg_df, data = surv_df)

# for JUST wounding:
w_df <- with(surv_df,
               data.frame(Crab_treatment = c("N", "N"), 
                          Algae_treatment = c("N", "N"),
                          Wounding_treatment = c("Y", "N")))

w.fit <- survfit(mCox, newdata = w_df, data = surv_df)

# for wounding AND crab interaction
CW_df <- with(surv_df,
                data.frame(Crab_treatment = c("Y", "Y", "N", "N"), 
                           Algae_treatment = c("N", "N", "N", "N"),
                           Wounding_treatment = c("Y", "N", "Y", "N")))

cw.fit <- survfit(mCox, newdata = CW_df, data = surv_df)



# plot them all
ggsurvplot(c.fit, conf.int = TRUE, legend.labs=c("Crab = Y", "Crab = N"),
           ggtheme = theme_classic())
ggsurvplot(cw.fit, conf.int = TRUE, legend.labs=c("Crab + Wounding", "Crab", "Wounding", "Control"),
           ggtheme = theme_classic())

arrange_ggsurvplots(list(
  ggsurvplot(c.fit, conf.int = TRUE, legend.labs=c("Yes", "Control"),
             ggtheme = theme_classic(), palette = c(skyB, lightO), 
             legend.title = "Crab", conf.int.alpha = 0.1, xlab="Time in days"),
  ggsurvplot(a.fit, legend.labs=c("Yes", "Control"),
             ggtheme = theme_classic(), palette = c(forGreen , lightO), 
             legend.title = "Algae", conf.int = TRUE, conf.int.alpha=0.1, 
             xlab="Time in days"),
  ggsurvplot(w.fit, data = surv_df, legend.labs=c("Yes", "Control"),
             ggtheme = theme_classic(), palette = c(darkO, lightO), 
             legend.title = "Wounding", conf.int = TRUE, conf.int.alpha=0.1, 
             xlab="Time in days"),
  ggsurvplot(cw.fit, legend.labs=c("Crab + Wounding", "Crab", "Wounding", "Control"),
             ggtheme = theme_classic(), 
             palette = c(vibRed, skyB, darkO, lightO), 
             legend.title = "Treatment", conf.int = TRUE, conf.int.alpha=0.1, 
             xlab="Time in days")),
  ncol = 2, nrow = 2) -> plts_coxph

# ggsave(here("figures/survivalCurves.pdf"), plts_coxph, width = 10, height = 8)

```

## Test model assumptions

We want to test that the hazards are proportional (don't change over time), which is assumed in the coxph model. We'll use scaled Schoenfled residuals, which are independent of time and should have a random pattern. The random assumption is supported by p > 0.05

```{r}
test.ph <- cox.zph(mCox) # meets this assumption
  ggcoxzph(test.ph) # no pattern with time
```

Then we'll test whether there's a strong outlier pull/influential observations

```{r}
ggcoxdiagnostics(mCox, type = "dfbeta", # dfbeta "plots the estimated changes in the regression coefficients upon deleting each observation in turn"
                 ggtheme = theme_bw()) 
```

- These look fairly symmetric so are going to leave everything as-is














