---
title: "Binomial tissue loss analysis"
author: "Julianna Renzi"
date: "12/7/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(tidyverse) # data manipulation
require(here) # relative file paths
require(lubridate) # dates and times
require(wesanderson) # color palette
require(broom) # logistic model fit
```

# Bring in the data

```{r}
# this is the daily previous mean maximum water temperatures with a 4-day window
tempMetrics <- read_csv(here("generated_data/temperature_metrics.csv"))

# this is the percent tissue loss on a nubbin on a given day (created in the tissue wrangling file)
tissueLoss <- read_csv(here("generated_data/tissue_loss.csv"))
```

Create our color palette from the Wes Anderson package

```{r}
vibRed <- wes_palette("Darjeeling1", n = 5)[1]
forGreen <- wes_palette("Darjeeling1", n = 5)[2]
lightO <- wes_palette("Darjeeling1", n = 5)[3]
darkO <- wes_palette("Darjeeling1", n = 5)[4]
skyB <- wes_palette("Darjeeling1", n = 5)[5]

```

# Make a tissue loss model that includes temperature

Before doing any analyses, we want to remove observations from February 4th because that represents tissue loss since the first (multiple days), which is not comparable to the rest. We also want to attach temperature observations to our tissue loss data

```{r}
# remove the 4th
tissueLoss %>% 
  filter(Date != as.Date("2020-02-04")) %>% 
  left_join(tempMetrics, key = Date) -> tissueLoss4

# do this without the "influential observation" (row 539 diagnosed using code below)
tissueLoss4.f <- tissueLoss4[-539,]
  

```

## Use a generalized linear model with a binomial family

Because of the large number of zeros in the dataset, we'll use a binomial response variable (0 for no tissue loss, 1 for tissue loss)

```{r}
# make a column for y/n tissue loss
tissueLoss4.f$TissueBin <- ifelse(tissueLoss4.f$Perc_tissue_loss > 0.0, 1, 0)

# make a model for the zeros
m1 <- glm(TissueBin ~ Crab_treatment*Algae_treatment*Wounding_treatment*Mean_C_4, 
          data = tissueLoss4.f, 
          family = binomial(link = logit))


step.bin <- step(m1, direction = "both")
  summary(step.bin)
```

Make model predictions

```{r}
# make a dataframe to store predictions in
pred <- expand.grid(Mean_C_4 = seq(min(tissueLoss4.f$Mean_C_4), max(tissueLoss4.f$Mean_C_4), by = 0.05), 
                    Crab_treatment = c("Y", "N"), 
                    Algae_treatment = c("Y", "N"), 
                    Wounding_treatment = c("Y", "N"))

# predict probability of ANY tissue loss
pred$PredProb <- predict(step.bin, pred, type = "response") # response gives the predicted probabilities 

```

Plot predictions

```{r}
# make labels nice
crab.labs <- c("Crab", "No crab")
names(crab.labs) <- c("Y", "N")


pred %>% 
  # use predicted data
  ggplot(aes(x = Mean_C_4, y = PredProb, color = Algae_treatment, linetype = Wounding_treatment)) +
  geom_line() +
  scale_linetype_manual(values=c("solid", "dashed"),
                        name = "Wounding") +
  # add in actual data
  geom_point(data = tissueLoss4.f, 
             aes(x = Mean_C_4, y = TissueBin, color = Algae_treatment), 
             alpha = 0.2) +
  facet_grid(.~Crab_treatment, labeller = labeller(Crab_treatment = crab.labs)) + # facet by crabs
  ylab("Predicted probability of losing tissue") +
  xlab("Average 4-day water temperature (°C)") +
  scale_color_manual(values = c(forGreen, darkO),
                     name = "Algae") +
  theme_classic()

```


# Check assumptions

## Linearity 

Need to see whether there's linearity using this tutorial: http://www.sthda.com/english/articles/36-classification-methods-essentials/148-logistic-regression-assumptions-and-diagnostics-in-r/

```{r}
# make predictions 
probabilities <- predict(step.bin, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")

# Select only numeric predictors
mydata <- tissueLoss4.f %>%
  dplyr::select(Mean_C_4)  

predictors <- colnames(mydata)

# Bind the logit and tidy the data for plotting
mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

# plot
ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "loess") + 
  theme_bw() + 
  facet_wrap(~predictors, scales = "free_y")
```

This generally looks linear to me, although it's a little weird because of the repeated temperature measures, I think

## Outliers

```{r}
# look for outliers
plot(step.bin, which = 4, id.n = 3)

# Extract model results
model.data <- augment(step.bin) %>% 
  mutate(index = 1:n()) 

model.data %>% top_n(3, .cooksd)


ggplot(model.data, aes(index, .std.resid)) + 
  geom_point(aes(color = TissueBin), alpha = .5) +
  theme_bw()

# look for influential points
model.data %>% 
  filter(abs(.std.resid) > 3) # this shows we're removed all "influential" observations (just one)
```



