---
title: "Temperature data wrangling"
author: "Julianna Renzi"
date: "9/28/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


# load packages
require(tidyverse) # data manipulation
require(here) # relative file paths
require(lubridate) # dates and times
```

# Bring in the temperature data from HOBO loggers and the associated metadata

In a previous script we turned the HOBO files into CSVs, which are stored in the CSVs folder in the HOBOs folder in the data folder of our project. There's a CSV for each logger, but for our purposes we want one dataframe with all of the temperature data.

We'll start by bringing in one CSV then doing that same process with a loop for the rest of the CSVs

```{r}
# first get list of all files we need to read in
hob_filelist <- list.files(here("data/HOBOs/CSVs")) 

# start with the first file on the list
hob_ID <- hob_filelist[1] 
hob_ID <- strsplit(hob_ID, "[.]") # get the file name separated from the .csv extension
hob_ID <- hob_ID[[1]][1] # get logger ID
name <- paste("h", hob_ID, sep="") # get name of the file that we'll use to refer to the csv (h for HOBO)

# rename columns to be more useful
name <- read_csv(here(paste("data/HOBOs/CSVs/", hob_filelist[1], sep = "")), skip=1) 
  colnames(name)[1] <- "Data_point"
  colnames(name)[2] <- "Date_time"
  colnames(name)[3] <- "Temp_C" 
  colnames(name)[4] <- "Intensity_lum_per_ft2" 
  
# make column into a datetime object to make it easier using lubridate
  # see https://evoldyn.gitlab.io/evomics-2018/ref-sheets/R_lubridate.pdf for more details
name$Date_time <- mdy_hms(name$Date_time)
name <- name[, c(1,2,3)] # remove End of File column/other columns so they don't get wacky in a row bind
name$Hobo_ID <- hob_ID
temp_data <- name

```

Now create the loop

```{r}
# use a loop to import all of the data

for (file in hob_filelist[-1]) { # skip the first file because that's what we did above
  hob_ID <- file
  hob_ID <- strsplit(hob_ID, "[.]")
  hob_ID <- hob_ID[[1]][1]
  name <- paste("h", hob_ID, sep="")
  name <- read_csv(here(paste("data/HOBOs/CSVs/", file, sep = "")), skip=1) # read in each csv
  colnames(name)[1] <- "Data_point" # re-name columns to match
  colnames(name)[2] <- "Date_time"
  colnames(name)[3] <- "Temp_C"
  colnames(name)[4] <- "Intensity_lum_per_ft2" 
  name$Date_time <- mdy_hms(name$Date_time) # make it a datetime object
  name <- name[, c(1,2,3)] 
  name$Hobo_ID <- hob_ID # add the hobo identifier
  temp_data <- bind_rows(temp_data, name)
}
  

```

Attach the metadata

```{r}
# Bring in the a key for logger tank position and site
hob_metadat <- read_csv(here("data/HOBOs/HOBO_metadata.csv"))

# want to make key the same format (both characters because tidyverse)
hob_metadat$Hobo_ID <- as.character(hob_metadat$Hobo_ID)

# and check to make sure the IDs match (no obvious typos)
l1 <- sort(unique(as.numeric(temp_data$Hobo_ID)))
l2 <- sort(unique(as.numeric(hob_metadat$Hobo_ID)))

for (id in l1){
  if (id %in% l2){
    print("YEET")
  } else {
    print("Nawhh")
  }
} 

# or:
l1 == l2

# then join the metadata to the temperature data
label_temp <- left_join(temp_data, hob_metadat, by="Hobo_ID") 
```

# Begin summarizing the temperature data

```{r}
# look for earliest date
label_temp$Date_time %>% min # Jan 26 (corals started acclimating )

label_temp %>% 
  filter(Tank != 21) %>% # don't want the control tank we didn't use
  filter(Date_time >=  as.Date("2020-01-27") & Date_time <  as.Date("2020-02-26")) %>% # just the experiment dates (include acclimation period so we can do 5 day previous summaries)
  mutate(Date_time = ifelse(Hobo_ID == as.character(10550960) & Date_time >  as.Date("2020-02-22"), NA, Date_time)) %>% 
  # get rid of loggers after the dates they were pulled
  # We're only keeping up to the date BEFORE they were pulled so there's no air temperature values from when they were pulled out
  mutate(Date_time = ifelse(Hobo_ID == as.character(10551953) & Date_time >  as.Date("2020-02-05"), NA, Date_time)) %>% 
  mutate(Date_time = ifelse(Hobo_ID == as.character(10551958) & Date_time >  as.Date("2020-02-11"), NA, Date_time)) %>% 
  filter(!is.na(Date_time)) %>% 
  mutate(Date_time = as_datetime(Date_time)) -> temp_filt_cumm # don't know why I have to do this again, but they converted back to numbers

```

Get an average temperature value per day-time across tanks

```{r}
temp_filt_cumm %>% 
  group_by(Date_time) %>% 
  summarise(Mean_temp = mean(Temp_C)) %>% 
  mutate(Day = date(Date_time)) -> temp_time_avgs # create a line for each day-time (can be multiple loggers recording at the same date-time, but want one value as a mean across tanks)
```

# Create cummulative metrics for the mean maximum temperature

Really heat stress accumulates, so it makes sense to summarize the few days leading up to an observation. We don't use degree heating days because our corals were acclimated to some shade cloths, which likely changed their thermal tolerance and thus chose to use max temperatures instead (still getting at the idea that the hot-hot temperatures are most important)

```{r}
temp_time_avgs %>% 
  group_by(Day) %>% 
  summarize(Max_C = max(Mean_temp)) %>% 
  mutate(Prev_max_C = lag(Max_C), 
         Max_C_2 = lag(Max_C) + lag(Max_C, 2),
         Max_C_3 = lag(Max_C) + lag(Max_C, 2) + lag(Max_C, 3),
         Max_C_4 = lag(Max_C) + lag(Max_C, 2) + lag(Max_C, 3) + lag(Max_C, 4), # stop at 4 because that's the max amount of time we have before the first observation
         # also we'll calculate the mean Max_C, which is probably more understandable (daily value)
         Mean_max_C_Prev = Prev_max_C,
         Mean_max_C_2 = Max_C_2/2,
         Mean_max_C_3 = Max_C_3/3,
         Mean_max_C_4 = Max_C_4/4) -> all_temp # df with cumulative mean max temperatures of preceding days 

```

# Save metrics to a CSV

Here we'll save the metric that we think is most interesting (4 day average maximum temperature).

```{r}
all_temp %>% 
  select(Day, Mean_max_C_4) %>% 
  rename(Date = Day) %>% # to match the response matrix
  drop_na() -> temp_metrics

```

Save as a CSV--remove the pound signs if you want to re-create the CSV. This first CSV is of the mean maximum temperatures

```{r}
# write_csv(x = temp_metrics, file = here("generated_data/temperature_metrics.csv"))
```

This second CSV is of the full temperature time series, but averaged across hobo loggers (1 value per date-time, NOT the mean daily value)

```{r}
# write_csv(x = temp_time_avgs, file = here("generated_data/hobo_timeseries.csv"))
```


