---
title: "Tissue loss vs. temperature plots"
author: "Julianna Renzi"
date: "11/7/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(tidyverse) # data manipulation
require(here) # relative file paths
require(lubridate) # dates and times
require(wesanderson) # color palette
require(patchwork) # combining figures
require(broom) # logistic model fit

require(lme4)
require(boot) # for inv.logit
```

# Bring in the data

```{r}
# this is the temperature time series from the experiment, with one value per date/time (averaged across HOBO loggers, with a value per few minutes)
tempTimeseries <- read_csv(here("generated_data/hobo_timeseries.csv"))

# this is the daily previous mean water temperatures (different temperature summary options)
tempMetrics <- read_csv(here("generated_data/temperature_metrics.csv"))

# this is the percent tissue loss on a nubbin on a given day (created in the tissue wrangling file)
tissueLoss <- read_csv(here("generated_data/tissue_loss.csv"))

```

Create our color palette from the Wes Anderson package

```{r}
vibRed <- wes_palette("Darjeeling1", n = 5)[1]
forGreen <- wes_palette("Darjeeling1", n = 5)[2]
lightO <- wes_palette("Darjeeling1", n = 5)[3]
darkO <- wes_palette("Darjeeling1", n = 5)[4]
skyB <- wes_palette("Darjeeling1", n = 5)[5]


# and specify text size
txt_sz <- 15 

```


# Plot temperature through time

Look at how the temperature changes over time

```{r}
tempTimeseries %>% 
  filter(Date_time > as_datetime("2020-02-01 00:00:00")) %>% # just from the start of the tissue loss data
  ggplot(aes(x = Date_time, y = Mean_temp)) +
  geom_line() +
  geom_hline(yintercept = 27.3, 
             color = vibRed, 
             linetype = "dotted") + # this is the Heron monthly mean water temp according to: https://seatemperature.info/heron-island-water-temperature.html and also word of mouth from Jesse + Gus
  theme_classic() +
  # make first rectangle highlighting the first peak 
  annotate("rect",
           xmin = as_datetime("2020-02-03 00:00:00"), 
           xmax = as_datetime("2020-02-08 00:00:00"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  annotate("rect",
           xmin = as_datetime("2020-02-15 00:00:00"), 
           xmax = as_datetime("2020-02-22 00:00:00"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  ylab("Water temperature (°C)") +
  xlab("") +
  ylim(26, 33)  +
  # change text size
  theme(text = element_text(size = txt_sz)) +
  ggtitle("(a)") -> tempTSFig
  

```

And how the mean 4-day window changes through time

```{r}
tempMetrics %>% 
  filter(Date > as.Date("2020-02-01", "%Y-%m-%d")) %>%  # just from the start of the tissue loss data
  ggplot(aes(x = Date, y = Mean_C_4)) +
  geom_line() +
  geom_hline(yintercept = 27.3, 
             color = vibRed, 
             linetype = "dotted") + # this is the Heron monthly mean water temp according to: https://seatemperature.info/heron-island-water-temperature.html and also word of mouth from Jesse + Gus
  theme_classic() +
  # make first rectangle highlighting the first peak 
  annotate("rect",
           xmin = as.Date("2020-02-03", "%Y-%m-%d"), 
           xmax = as.Date("2020-02-08", "%Y-%m-%d"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  annotate("rect",
           xmin = as.Date("2020-02-15", "%Y-%m-%d"), 
           xmax = as.Date("2020-02-22", "%Y-%m-%d"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  ylab("Mean temperature-4 day (°C)") +
  xlab("") +
  # change text size
  theme(text = element_text(size = txt_sz)) +
  ggtitle("(b)") -> meanTSFig

```


# Plot tissue loss through time

Get the average tissue loss by treatment (average tissue loss across the treatment group on a given day)

```{r}
tissueLoss %>% 
  # update this for the first day of the experiment (no tissue loss)
  mutate(Date = case_when(
    Date == as.Date("2020-01-31") ~ as.Date("2020-02-01"),
    TRUE ~ Date)) %>% 
  group_by(Crab_treatment, Algae_treatment, Wounding_treatment, Date) %>%
  summarize(MeanTL = mean(Perc_tissue_loss)) -> avgTL
```


Then plot the data through time, broken up by treatments

```{r}
# make labels nice
crab.labs <- c("Crab", "No crab")
names(crab.labs) <- c("Y", "N")


avgTL %>%
  ggplot(aes(x = Date, y = MeanTL, color = Algae_treatment, linetype = Wounding_treatment)) +
  geom_line() +
  scale_linetype_manual(values=c("solid", "dashed"),
                        name = "Wounding") +
  facet_grid(.~Crab_treatment, labeller = labeller(Crab_treatment = crab.labs)) + # facet by crabs
  ylab("Average tissue loss (%)") +
  xlab("") +
  scale_color_manual(values = c(darkO, forGreen),
                     name = "Algae") + # clean up legend and colors
  theme_classic() +
  # add rectangles showing extreme heat periods
  annotate("rect",
           xmin = as.Date("2020-02-03", "%Y-%m-%d"), 
           xmax = as.Date("2020-02-08", "%Y-%m-%d"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  annotate("rect",
           xmin = as.Date("2020-02-15 00:00:00", "%Y-%m-%d"), 
           xmax = as.Date("2020-02-22 00:00:00", "%Y-%m-%d"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  # change text size
  theme(text = element_text(size = txt_sz)) +
  ggtitle("(c)") -> tissueLFig
```


# Make a tissue loss model that includes temperature

Before doing any analyses, we want to remove observations from February 4th because that represents tissue loss since the first (multiple days), which is not comparable to the rest. We also want to attach temperature observations to our tissue loss data and remove one influential observation (row 539) found using Cook's distance

```{r}
# remove the 4th
tissueLoss %>% 
  filter(Date != as.Date("2020-02-04")) %>% 
  # update this for the first day of the experiment (no tissue loss)
  mutate(Date = case_when(
    Date == as.Date("2020-01-31") ~ as.Date("2020-02-01"),
    TRUE ~ Date)) %>% 
  left_join(tempMetrics, key = Date) -> tissueLoss4

# we also want to remove the "influential observation" (row 539 diagnosed using code below)
tissueLoss4.f <- tissueLoss4[-539,]
```

## Use a generalized linear model with a binomial family

Because of the large number of zeros in the dataset, we'll use a binomial response variable (0 for no tissue loss, 1 for tissue loss)

```{r}
# make a column for y/n tissue loss
tissueLoss4.f$TissueBin <- ifelse(tissueLoss4.f$Perc_tissue_loss > 0.0, 1, 0)
  
```

Make the full mixed model

```{r}
# make a mixed model for the zeros
m1 <- glmer(TissueBin ~ Crab_treatment*Algae_treatment*Wounding_treatment*scale(Mean_C_4) + (1|Coral_ID), 
          data = tissueLoss4.f, 
          family = "binomial",
          control=glmerControl(optimizer = "bobyqa", 
                               optCtrl = list(maxfun=2e5))) # this last line just helps it fit 

summary(m1)
```



## Check assumptions

### Linearity 

Need to see whether there's linearity using this tutorial: http://www.sthda.com/english/articles/36-classification-methods-essentials/148-logistic-regression-assumptions-and-diagnostics-in-r/

```{r}
# make predictions 
probabilities <- predict(m1, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")

# Select only numeric predictors
mydata <- tissueLoss4.f %>%
  dplyr::select(Mean_C_4)  

predictors <- colnames(mydata)

# Bind the logit and tidy the data for plotting
mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

# plot
ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "loess") + 
  theme_bw() + 
  facet_wrap(~predictors, scales = "free_y")
```

This generally looks linear to me, although it's a little weird because of the repeated temperature measures

### Outliers

```{r}
# Extract model results
model.data <- augment(m1) %>% 
  mutate(index = 1:n()) 

model.data %>% top_n(3, .cooksd)


ggplot(model.data, aes(index, .std.resid)) + 
  geom_point(aes(color = TissueBin), alpha = .5) +
  theme_bw()

# look for influential points
model.data %>% 
  filter(abs(.std.resid) > 3) # this shows there are no "influential" observations 
```



### Plot predictions

```{r}
# make labels nice
crab.labs <- c("Crab", "No crab")
names(crab.labs) <- c("Y", "N")



# make a dataframe to store predictions in
pred <- expand.grid(Mean_C_4 = seq(min(tissueLoss4.f$Mean_C_4), max(tissueLoss4.f$Mean_C_4), by = 0.05), 
                    Crab_treatment = c("Y", "N"), 
                    Algae_treatment = c("Y", "N"), 
                    Wounding_treatment = c("Y", "N"),
                    Coral_ID = 1:80)

# generate predictions
pred$PredProb <- predict(m1, pred, type = "response")

# get the average across corals
pred %>% 
  group_by(Crab_treatment, Algae_treatment, Wounding_treatment, Mean_C_4) %>% 
  summarize(Mean_prob = mean(PredProb), SE = sd(PredProb)/sqrt(n())) -> pred_avg


# plot
pred_avg %>% 
  # use predicted data
  ggplot(aes(x = Mean_C_4, y = Mean_prob, color = Algae_treatment, linetype = Wounding_treatment)) +
  geom_line() +
  scale_linetype_manual(values=c("dashed", "solid"),
                        name = "Wounding") +
  # add in actual data
  geom_point(data = tissueLoss4.f, 
             aes(x = Mean_C_4, y = TissueBin, color = Algae_treatment), 
             alpha = 0.2) +
  facet_grid(.~Crab_treatment, labeller = labeller(Crab_treatment = crab.labs)) + # facet by crabs
  ylab("Predicted probability of losing tissue") +
  xlab("Average 4-day water temperature (°C)") +
  scale_color_manual(values = c(forGreen, darkO),
                     name = "Algae") +
  theme_classic() +
  # change text size
  theme(text = element_text(size = txt_sz)) +
  ggtitle("(d)") -> modelfig

```

# Combine figures 

To save these figures as a PDF in the figures folder, remove the pound signs before the `pdf()` and `dev.off()`

```{r}
# pdf(file = here("figures/tissueLTempseries.pdf"), width = 9.5, height = 11)

(tempTSFig + meanTSFig) / (tissueLFig) / (modelfig) 

# dev.off()
```


# Make an interactions plot

First, get the coefficients from our full model

```{r}
# get fixed effects 
intercept <- as.numeric(fixef(m1)[1]) # intercept
C <- as.numeric(fixef(m1)[2]) # crab
A <- as.numeric(fixef(m1)[3]) # algae
W <- as.numeric(fixef(m1)[4]) # wounding
Temp <- as.numeric(fixef(m1)[5]) # temperature (scaled)
CA <- as.numeric(fixef(m1)[6]) # crab:algae
CW <- as.numeric(fixef(m1)[7]) # crab:wounding
AW <- as.numeric(fixef(m1)[8]) # algae:wounding
CTemp <- as.numeric(fixef(m1)[9]) # crab:temp
ATemp <- as.numeric(fixef(m1)[10]) # algae:temp
WTemp <- as.numeric(fixef(m1)[11]) # wounding:temp
CAW <- as.numeric(fixef(m1)[12]) # crab:algae:wounding
CATemp <- as.numeric(fixef(m1)[13]) # crab:algae:temp
CWTemp <- as.numeric(fixef(m1)[14]) # crab:wounding:temp
AWTemp <- as.numeric(fixef(m1)[15]) # algae:wounding:temp
CAWTemp <- as.numeric(fixef(m1)[16]) # crab:algae:wounding:temp



```

Then, use the equation from the model to plot the sum of the interactions (no main effects) over a range of temperature values

```{r}
# get the value of temperatures we want to predict over
temp_range <- unique(scale(tissueLoss4.f$Mean_C_4))

# make a tibble to hold data
int_table <- tibble(
  T_range = temp_range
)

```

Full interaction equation looks like: 

*intercept + CA + CW + AW + CTemp + ATemp + WTemp + CAW + CATemp + CWTemp + AWTemp + CAWTemp*
- A term goes away if it's not in the interaction 

```{r}
# look at the effects of just the interactions (no fixed effects) to determine synergy/antagonism/etc.

# generate a function that will generate the effect
# this only works if you've specified C/CA/etc. above (could change that) and it is specific to our model
get_interaction <- function(Crab_p, Algae_p, Wounding_p, Temp_p, Temp_range) {
  # the parameters are all presences ("p") of each treatment
  impact <- 
    (CA*Crab_p*Algae_p) + 
    (CW*Crab_p*Wounding_p) + 
    (AW*Algae_p*Wounding_p) + 
    (CTemp*Crab_p*Temp_p)*Temp_range + 
    (ATemp*Algae_p*Temp_p)*Temp_range + 
    (WTemp*Wounding_p*Temp_p)*Temp_range + 
    (CAW*Crab_p*Algae_p*Wounding_p) + 
    (CATemp*Crab_p*Algae_p*Temp_p)*Temp_range + 
    (CWTemp*Crab_p*Wounding_p*Temp_p)*Temp_range + 
    (AWTemp*Algae_p*Wounding_p*Temp_p)*Temp_range + 
    (CAWTemp*Crab_p*Algae_p*Wounding_p*Temp_p)*Temp_range
  
  return(impact)
}


# make sure it works by hand for Crab:Algae:Temperature (no wounding)
crabalgT <- (CA + CTemp*temp_range + ATemp*temp_range + CATemp*temp_range) # removed intercept

# make sure they're the same:
(crabalgT) == get_interaction(Crab_p = 1, Algae_p = 1, Temp_p = 1, Wounding_p = 0, Temp_range = temp_range) # nice!

```

## Generate interaction estimates across a temperature range

```{r}
# make columns for different interactions
int_table %>% 
  mutate(C_A_T = get_interaction(Crab_p = 1, 
                                    Algae_p = 1, 
                                    Temp_p = 1, 
                                    Wounding_p = 0, 
                                    Temp_range = temp_range),
         C_W_T = get_interaction(Crab_p = 1, 
                                    Algae_p = 0, 
                                    Temp_p = 1, 
                                    Wounding_p = 1, 
                                    Temp_range = temp_range),
         A_W_T = get_interaction(Crab_p = 0, 
                                    Algae_p = 1, 
                                    Temp_p = 1, 
                                    Wounding_p = 1, 
                                    Temp_range = temp_range),
         C_A_W = get_interaction(Crab_p = 1, 
                                    Algae_p = 1, 
                                    Temp_p = 0, 
                                    Wounding_p = 1, 
                                    Temp_range = temp_range),
         C_A = get_interaction(Crab_p = 1, 
                                    Algae_p = 1, 
                                    Temp_p = 0, 
                                    Wounding_p = 0, 
                                    Temp_range = temp_range),
         C_W = get_interaction(Crab_p = 1, 
                                    Algae_p = 0, 
                                    Temp_p = 0, 
                                    Wounding_p = 1, 
                                    Temp_range = temp_range),
         A_W = get_interaction(Crab_p = 0, 
                                    Algae_p = 1, 
                                    Temp_p = 0, 
                                    Wounding_p = 1, 
                                    Temp_range = temp_range),
         C_T = get_interaction(Crab_p = 1, 
                                    Algae_p = 0, 
                                    Temp_p = 1, 
                                    Wounding_p = 0, 
                                    Temp_range = temp_range),
         A_T = get_interaction(Crab_p = 0, 
                                    Algae_p = 1, 
                                    Temp_p = 1, 
                                    Wounding_p = 0, 
                                    Temp_range = temp_range),
         W_T = get_interaction(Crab_p = 0, 
                                    Algae_p = 0, 
                                    Temp_p = 1, 
                                    Wounding_p = 1, 
                                    Temp_range = temp_range),
         C_A_W_T = get_interaction(Crab_p = 1, 
                                    Algae_p = 1, 
                                    Temp_p = 1, 
                                    Wounding_p = 1, 
                                    Temp_range = temp_range)) -> int_effects
```

Change the values into long format so they're easier to plot

```{r}
int_effects %>% 
  pivot_longer(cols = c(2:length(int_effects)),
               names_to = "Interactions",
               values_to = "Log_odds") %>% 
  # add columns to separate these out
  mutate(Crab = case_when(str_detect(Interactions, pattern = "C") ~ "Y", TRUE ~ "N"),
         Algae = case_when(str_detect(Interactions, pattern = "A") ~ "Y", TRUE ~ "N"),
         Wounding = case_when(str_detect(Interactions, pattern = "W") ~ "Y", TRUE ~ "N"),
         Temperature = case_when(str_detect(Interactions, pattern = "T") ~ "Y", TRUE ~ "N")) -> int_plot
```


A reminder from the internet: "An odds ratio of 1.46 means Smoking multiplies by 1.46 the probability of having heart disease compared to non-smokers. If β = – 0.38, then eβ = 0.68 and the interpretation becomes: smoking is associated with a 32% (1 – 0.68 = 0.32) reduction in the relative risk of heart disease."

Log odds (what we plot below) is neutral at 0, then is less likely in negatives and more likely in positives

## Get standard errors

Make a function that will estimate the variance of a combination of linear terms using this equation: https://stats.stackexchange.com/questions/160230/variance-of-linear-combinations-of-correlated-random-variables 

```{r}
get_variance <- function(Crab_p, Algae_p, Wounding_p, Temp_p, Temp_range, vcov_matrix) { 
  # create a function to get the variance of a linear combination of correlated random variables
  # the parameters are all presences ("p") of each treatment (should be a 1 or 0)
  # temp_range is a vector of *scaled* temperature values you want variances for 
  # vcov_matrix = a variance covariance matrix from the model. Can get from vcov(model)
  
  # coeff_matrix = this is a matrix of 11 columns (or # of terms you have) by 50 rows (or however many temperature values you want to predict for). Terms included should be "1" down the column and terms excluded should be "0". Terms with temperature should use the temperature range
  coeff_matrix <- matrix(0, nrow = length(Temp_range), ncol = dim(vcov_matrix)[1])
  colnames(coeff_matrix) <- colnames(vcov_matrix) # add names back
  
  
  # put zeros where needed
  # for main effects (just looking at interaction terms)
  coeff_matrix[,1:5]=0
  # for other terms:
  coeff_matrix[,"Crab_treatmentY:Algae_treatmentY"] = Crab_p*Algae_p
  coeff_matrix[,"Crab_treatmentY:Wounding_treatmentY"] = Crab_p*Wounding_p
  coeff_matrix[,"Algae_treatmentY:Wounding_treatmentY"] = Algae_p*Wounding_p
  coeff_matrix[,"Crab_treatmentY:scale(Mean_C_4)"] = Crab_p*Temp_range
  coeff_matrix[,"Algae_treatmentY:scale(Mean_C_4)"] = Algae_p*Temp_range
  coeff_matrix[,"Wounding_treatmentY:scale(Mean_C_4)"] = Wounding_p*Temp_range
  coeff_matrix[,"Crab_treatmentY:Algae_treatmentY:Wounding_treatmentY"] = Crab_p*Algae_p*Wounding_p
  coeff_matrix[,"Crab_treatmentY:Algae_treatmentY:scale(Mean_C_4)"] = Crab_p*Algae_p*Temp_range
  coeff_matrix[,"Crab_treatmentY:Wounding_treatmentY:scale(Mean_C_4)"] = Crab_p*Wounding_p*Temp_range
  coeff_matrix[,"Algae_treatmentY:Wounding_treatmentY:scale(Mean_C_4)"] = Algae_p*Wounding_p*Temp_range
  coeff_matrix[,"Crab_treatmentY:Algae_treatmentY:Wounding_treatmentY:scale(Mean_C_4)"] = Crab_p*Algae_p*Wounding_p*Temp_range
  
  
  # loop through to get the variance
  variance_sum <- rep(0, times = length(Temp_range)) # initialize
  # loop
  for (i in 1:dim(vcov_matrix)[1]) {
    for (j in 1:dim(vcov_matrix)[2]) {
      variance_sum = variance_sum + coeff_matrix[,i]*coeff_matrix[,j]*vcov_matrix[i,j]
    }
  }
  
  return(variance_sum)
  
}
```


Test it

```{r}
get_variance(Crab_p = 1, Algae_p = 1, Wounding_p = 0, Temp_p = 1, Temp_range = seq(-1.5, 1.5, length.out = 40), vcov_matrix = vcov(m1))
```


Compare to by hand

```{r}
vcov.m1 <- vcov(m1)
Temp_range <- seq(-1.5, 1.5, length.out = 40)

vcov.m1["Crab_treatmentY:Algae_treatmentY", "Crab_treatmentY:Algae_treatmentY"] + vcov.m1["Crab_treatmentY:scale(Mean_C_4)", "Crab_treatmentY:scale(Mean_C_4)"]*Temp_range^2 +
  vcov.m1["Algae_treatmentY:scale(Mean_C_4)", "Algae_treatmentY:scale(Mean_C_4)"]*Temp_range^2 +
  vcov.m1["Crab_treatmentY:Algae_treatmentY:scale(Mean_C_4)", "Crab_treatmentY:Algae_treatmentY:scale(Mean_C_4)"]*Temp_range^2 +
  vcov.m1["Crab_treatmentY:Algae_treatmentY", "Crab_treatmentY:scale(Mean_C_4)"]*2*Temp_range +
  vcov.m1["Crab_treatmentY:Algae_treatmentY", "Algae_treatmentY:scale(Mean_C_4)"]*2*Temp_range +
  vcov.m1["Crab_treatmentY:scale(Mean_C_4)", "Algae_treatmentY:scale(Mean_C_4)"]*2*Temp_range*Temp_range +
  vcov.m1["Crab_treatmentY:Algae_treatmentY:scale(Mean_C_4)", "Crab_treatmentY:scale(Mean_C_4)"]*2*Temp_range*Temp_range +
  vcov.m1["Crab_treatmentY:Algae_treatmentY", "Crab_treatmentY:Algae_treatmentY:scale(Mean_C_4)"]*2*Temp_range +
  vcov.m1["Crab_treatmentY:Algae_treatmentY:scale(Mean_C_4)", "Algae_treatmentY:scale(Mean_C_4)"]*2*Temp_range*Temp_range
  
  
  
```



## Try to plot?

Get variances for the lines. Should be sqrt(variance)*1.96 for 95% CIs (sample size is included in variance in this case). Add this to the int_plot data frame

```{r}
int_plot %>% 
  # first change to 0's/1's for the input to the function
  mutate(Crab = case_when(Crab == "Y" ~ 1,
                          Crab == "N" ~ 0)) %>% 
  mutate(Wounding = case_when(Wounding == "Y" ~ 1,
                              Wounding == "N" ~ 0)) %>% 
  mutate(Algae = case_when(Algae == "Y" ~ 1,
                           Algae == "N" ~ 0)) %>% 
  mutate(Temperature = case_when(Temperature == "Y" ~ 1,
                                 Temperature == "N" ~ 0)) %>% 
  # call our function
  mutate(Variance = get_variance(Crab_p = Crab, 
                                 Algae_p = Algae, 
                                 Wounding_p = Wounding, 
                                 Temp_p = Temperature, 
                                 Temp_range = T_range,
                                 vcov_matrix = vcov(m1))) %>% 
  mutate(CI95 = 1.96*sqrt(Variance)) -> int_variance

# clean up the dataframe by switching factors back to factors (better for plotting/treating as factors)
int_variance %>% 
  select(-Crab, -Wounding, -Algae, -Temperature) %>% 
  left_join(int_plot, by = c("T_range", "Interactions", "Log_odds")) -> int_variance_fact
```

## Plot interactions

```{r}
 pdf(file = here("figures/interactions.pdf"), width = 8, height = 6)

int_variance_fact %>% 
  filter(Temperature == "Y") %>% 
  ggplot(aes(x = T_range, y = Log_odds, color = Wounding, linetype = Wounding)) +
  scale_color_manual(values = c(lightO, skyB),
                     name = "Wounding") + 
  geom_line() +
  geom_hline(yintercept = 0) +
  scale_linetype_manual(values=c("solid", "dashed"),
                        name = "Wounding") +
  
  geom_ribbon(aes(ymin=Log_odds-CI95, ymax=Log_odds+CI95, fill = Wounding), alpha = 0.5) +
  scale_fill_manual(values = c(lightO, skyB),
                     name = "Wounding") +
  
  ylab("Change in log odds of tissue loss") +
  xlab("Temperature (scaled)") +
  theme_classic() +
  theme(text = element_text(size = txt_sz)) +
  facet_grid(Crab ~Algae, labeller = label_both) 

 dev.off()
  
```


