---
title: "Tissue loss vs. temperature plots"
author: "Julianna Renzi"
date: "11/7/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(tidyverse) # data manipulation
require(here) # relative file paths
require(lubridate) # dates and times
require(wesanderson) # color palette
require(patchwork) # combining figures
require(broom) # logistic model fit
```

# Bring in the data

```{r}
# this is the temperature time series from the experiment, with one value per date/time (averaged across HOBO loggers, with a value per few minutes)
tempTimeseries <- read_csv(here("generated_data/hobo_timeseries.csv"))

# this is the daily previous mean water temperatures (different temperature summary options)
tempMetrics <- read_csv(here("generated_data/temperature_metrics.csv"))

# this is the percent tissue loss on a nubbin on a given day (created in the tissue wrangling file)
tissueLoss <- read_csv(here("generated_data/tissue_loss.csv"))

```

Create our color palette from the Wes Anderson package

```{r}
vibRed <- wes_palette("Darjeeling1", n = 5)[1]
forGreen <- wes_palette("Darjeeling1", n = 5)[2]
lightO <- wes_palette("Darjeeling1", n = 5)[3]
darkO <- wes_palette("Darjeeling1", n = 5)[4]
skyB <- wes_palette("Darjeeling1", n = 5)[5]

```


# Plot temperature through time

Look at how the temperature changes over time

```{r}
tempTimeseries %>% 
  filter(Date_time > as_datetime("2020-02-03 00:00:00")) %>% # just from the start of the tissue loss data
  ggplot(aes(x = Date_time, y = Mean_temp)) +
  geom_line() +
  geom_hline(yintercept = 27.3, 
             color = vibRed, 
             linetype = "dotted") + # this is the Heron monthly mean water temp according to: https://seatemperature.info/heron-island-water-temperature.html and also word of mouth from Jesse + Gus
  theme_classic() +
  # make first rectangle highlighting the first peak 
  annotate("rect",
           xmin = as_datetime("2020-02-03 00:00:00"), 
           xmax = as_datetime("2020-02-08 00:00:00"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  annotate("rect",
           xmin = as_datetime("2020-02-15 00:00:00"), 
           xmax = as_datetime("2020-02-22 00:00:00"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  ylab("Water temperature (°C)") +
  xlab("Date") +
  ylim(26, 33) -> tempTSFig
  

```

And how the mean 4-day window changes through time

```{r}
tempMetrics %>% 
  filter(Date > as.Date("2020-01-31", "%Y-%m-%d")) %>%  # just from the start of the tissue loss data
  ggplot(aes(x = Date, y = Mean_C_4)) +
  geom_line() +
  geom_hline(yintercept = 27.3, 
             color = vibRed, 
             linetype = "dotted") + # this is the Heron monthly mean water temp according to: https://seatemperature.info/heron-island-water-temperature.html and also word of mouth from Jesse + Gus
  theme_classic() +
  # make first rectangle highlighting the first peak 
  annotate("rect",
           xmin = as.Date("2020-02-03", "%Y-%m-%d"), 
           xmax = as.Date("2020-02-08", "%Y-%m-%d"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  annotate("rect",
           xmin = as.Date("2020-02-15", "%Y-%m-%d"), 
           xmax = as.Date("2020-02-22", "%Y-%m-%d"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  ylab("Mean temperature-4 day (°C)") +
  xlab("Date") -> meanTSFig

```


# Plot tissue loss through time

Get the average tissue loss by treatment (average tissue loss across the treatment group on a given day)

```{r}
tissueLoss %>% 
  group_by(Crab_treatment, Algae_treatment, Wounding_treatment, Date) %>% 
  summarize(MeanTL = mean(Perc_tissue_loss)) -> avgTL
```


Then plot the data through time, broken up by treatments

```{r}
# make labels nice
crab.labs <- c("Crab", "No crab")
names(crab.labs) <- c("Y", "N")


avgTL %>%
  ggplot(aes(x = Date, y = MeanTL, color = Algae_treatment, linetype = Wounding_treatment)) +
  geom_line() +
  scale_linetype_manual(values=c("solid", "dashed"),
                        name = "Wounding") +
  facet_grid(.~Crab_treatment, labeller = labeller(Crab_treatment = crab.labs)) + # facet by crabs
  ylab("Average tissue loss (%)") +
  xlab("Date") +
  scale_color_manual(values = c(darkO, forGreen),
                     name = "Algae") + # clean up legend and colors
  theme_classic() +
  # add rectangles showing extreme heat periods
  annotate("rect",
           xmin = as.Date("2020-02-03", "%Y-%m-%d"), 
           xmax = as.Date("2020-02-08", "%Y-%m-%d"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  annotate("rect",
           xmin = as.Date("2020-02-15 00:00:00", "%Y-%m-%d"), 
           xmax = as.Date("2020-02-22 00:00:00", "%Y-%m-%d"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) -> tissueLFig
```


# Make a tissue loss model that includes temperature

Before doing any analyses, we want to remove observations from February 4th because that represents tissue loss since the first (multiple days), which is not comparable to the rest. We also want to attach temperature observations to our tissue loss data and remove one influential observation (row 539) found using Cook's distance

```{r}
# remove the 4th
tissueLoss %>% 
  filter(Date != as.Date("2020-02-04")) %>% 
  left_join(tempMetrics, key = Date) -> tissueLoss4

# we also want to remove the "influential observation" (row 539 diagnosed using code below)
tissueLoss4.f <- tissueLoss4[-539,]
```

## Use a generalized linear model with a binomial family

Because of the large number of zeros in the dataset, we'll use a binomial response variable (0 for no tissue loss, 1 for tissue loss)

```{r}
# make a column for y/n tissue loss
tissueLoss4.f$TissueBin <- ifelse(tissueLoss4.f$Perc_tissue_loss > 0.0, 1, 0)

# make a model for the zeros
m1 <- glm(TissueBin ~ Crab_treatment*Algae_treatment*Wounding_treatment*Mean_C_4, 
          data = tissueLoss4.f, 
          family = binomial(link = logit))


step.bin <- step(m1, direction = "both")
  summary(step.bin)
```

Make model predictions

```{r}
# make a dataframe to store predictions in
pred <- expand.grid(Mean_C_4 = seq(min(tissueLoss4.f$Mean_C_4), max(tissueLoss4.f$Mean_C_4), by = 0.05), 
                    Crab_treatment = c("Y", "N"), 
                    Algae_treatment = c("Y", "N"), 
                    Wounding_treatment = c("Y", "N"))

# predict probability of ANY tissue loss
pred$PredProb <- predict(step.bin, pred, type = "response") # response gives the predicted probabilities 

```

### Plot predictions

```{r}
# make labels nice
crab.labs <- c("Crab", "No crab")
names(crab.labs) <- c("Y", "N")


pred %>% 
  # use predicted data
  ggplot(aes(x = Mean_C_4, y = PredProb, color = Algae_treatment, linetype = Wounding_treatment)) +
  geom_line() +
  scale_linetype_manual(values=c("solid", "dashed"),
                        name = "Wounding") +
  # add in actual data
  geom_point(data = tissueLoss4.f, 
             aes(x = Mean_C_4, y = TissueBin, color = Algae_treatment), 
             alpha = 0.2) +
  facet_grid(.~Crab_treatment, labeller = labeller(Crab_treatment = crab.labs)) + # facet by crabs
  ylab("Predicted probability of losing tissue") +
  xlab("Average 4-day water temperature (°C)") +
  scale_color_manual(values = c(forGreen, darkO),
                     name = "Algae") +
  theme_classic() -> modelfig

```


**Observations from the plot**
See that: 
- Temperature generally increases the probability of losing tissue
- Having algal contact increases the probability of losing tissue
- Wounding increases tissue loss without a crab, but decreases tissue loss with a crab (like survival results)
- The effect of temperature (slope) is less when there is a crab present and when there is no algae present (looks about parallel with no algae + crab)
- Temperature had the largest effect on tissue loss when there was no crab, algae, and wounding


# Check assumptions

## Linearity 

Need to see whether there's linearity using this tutorial: http://www.sthda.com/english/articles/36-classification-methods-essentials/148-logistic-regression-assumptions-and-diagnostics-in-r/

```{r}
# make predictions 
probabilities <- predict(step.bin, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")

# Select only numeric predictors
mydata <- tissueLoss4.f %>%
  dplyr::select(Mean_C_4)  

predictors <- colnames(mydata)

# Bind the logit and tidy the data for plotting
mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

# plot
ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "loess") + 
  theme_bw() + 
  facet_wrap(~predictors, scales = "free_y")
```

This generally looks linear to me, although it's a little weird because of the repeated temperature measures, I think

## Outliers

```{r}
# look for outliers
plot(step.bin, which = 4, id.n = 3)

# Extract model results
model.data <- augment(step.bin) %>% 
  mutate(index = 1:n()) 

model.data %>% top_n(3, .cooksd)


ggplot(model.data, aes(index, .std.resid)) + 
  geom_point(aes(color = TissueBin), alpha = .5) +
  theme_bw()

# look for influential points
model.data %>% 
  filter(abs(.std.resid) > 3) # this shows we're removed all "influential" observations (just one)
```


# Combine figures 

To save these figures as a PDF in the figures folder, remove the pound signs before the `pdf()` and `dev.off()`

```{r}
# pdf(file = here("figures/tissueLTempseries.pdf"), width = 8.5, height = 10)

(tempTSFig + meanTSFig) / (tissueLFig) / (modelfig)

# dev.off()
```

