---
title: "Tissue loss vs. temperature plots"
author: "Julianna Renzi"
date: "11/7/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(tidyverse) # data manipulation
require(here) # relative file paths
require(lubridate) # dates and times
require(wesanderson) # color palette
require(patchwork) # combining figures
require(broom) # logistic model fit
```

# Bring in the data

```{r}
# this is the temperature time series from the experiment, with one value per date/time (averaged across HOBO loggers, with a value per few minutes)
tempTimeseries <- read_csv(here("generated_data/hobo_timeseries.csv"))

# this is the daily previous mean water temperatures (different temperature summary options)
tempMetrics <- read_csv(here("generated_data/temperature_metrics.csv"))

# this is the percent tissue loss on a nubbin on a given day (created in the tissue wrangling file)
tissueLoss <- read_csv(here("generated_data/tissue_loss.csv"))

```

Create our color palette from the Wes Anderson package

```{r}
vibRed <- wes_palette("Darjeeling1", n = 5)[1]
forGreen <- wes_palette("Darjeeling1", n = 5)[2]
lightO <- wes_palette("Darjeeling1", n = 5)[3]
darkO <- wes_palette("Darjeeling1", n = 5)[4]
skyB <- wes_palette("Darjeeling1", n = 5)[5]


# and specify text size
txt_sz <- 15 

```


# Plot temperature through time

Look at how the temperature changes over time

```{r}
tempTimeseries %>% 
  filter(Date_time > as_datetime("2020-02-01 00:00:00")) %>% # just from the start of the tissue loss data
  ggplot(aes(x = Date_time, y = Mean_temp)) +
  geom_line() +
  geom_hline(yintercept = 27.3, 
             color = vibRed, 
             linetype = "dotted") + # this is the Heron monthly mean water temp according to: https://seatemperature.info/heron-island-water-temperature.html and also word of mouth from Jesse + Gus
  theme_classic() +
  # make first rectangle highlighting the first peak 
  annotate("rect",
           xmin = as_datetime("2020-02-03 00:00:00"), 
           xmax = as_datetime("2020-02-08 00:00:00"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  annotate("rect",
           xmin = as_datetime("2020-02-15 00:00:00"), 
           xmax = as_datetime("2020-02-22 00:00:00"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  ylab("Water temperature (°C)") +
  xlab("") +
  ylim(26, 33)  +
  # change text size
  theme(text = element_text(size = txt_sz)) +
  ggtitle("(a)") -> tempTSFig
  

```

And how the mean 4-day window changes through time

```{r}
tempMetrics %>% 
  filter(Date > as.Date("2020-02-01", "%Y-%m-%d")) %>%  # just from the start of the tissue loss data
  ggplot(aes(x = Date, y = Mean_C_4)) +
  geom_line() +
  geom_hline(yintercept = 27.3, 
             color = vibRed, 
             linetype = "dotted") + # this is the Heron monthly mean water temp according to: https://seatemperature.info/heron-island-water-temperature.html and also word of mouth from Jesse + Gus
  theme_classic() +
  # make first rectangle highlighting the first peak 
  annotate("rect",
           xmin = as.Date("2020-02-03", "%Y-%m-%d"), 
           xmax = as.Date("2020-02-08", "%Y-%m-%d"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  annotate("rect",
           xmin = as.Date("2020-02-15", "%Y-%m-%d"), 
           xmax = as.Date("2020-02-22", "%Y-%m-%d"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  ylab("Mean temperature-4 day (°C)") +
  xlab("") +
  # change text size
  theme(text = element_text(size = txt_sz)) +
  ggtitle("(b)") -> meanTSFig

```


# Plot tissue loss through time

Get the average tissue loss by treatment (average tissue loss across the treatment group on a given day)

```{r}
tissueLoss %>% 
  # update this for the first day of the experiment (no tissue loss)
  mutate(Date = case_when(
    Date == as.Date("2020-01-31") ~ as.Date("2020-02-01"),
    TRUE ~ Date)) %>% 
  group_by(Crab_treatment, Algae_treatment, Wounding_treatment, Date) %>%
  summarize(MeanTL = mean(Perc_tissue_loss)) -> avgTL
```


Then plot the data through time, broken up by treatments

```{r}
# make labels nice
crab.labs <- c("Crab", "No crab")
names(crab.labs) <- c("Y", "N")


avgTL %>%
  ggplot(aes(x = Date, y = MeanTL, color = Algae_treatment, linetype = Wounding_treatment)) +
  geom_line() +
  scale_linetype_manual(values=c("solid", "dashed"),
                        name = "Wounding") +
  facet_grid(.~Crab_treatment, labeller = labeller(Crab_treatment = crab.labs)) + # facet by crabs
  ylab("Average tissue loss (%)") +
  xlab("") +
  scale_color_manual(values = c(darkO, forGreen),
                     name = "Algae") + # clean up legend and colors
  theme_classic() +
  # add rectangles showing extreme heat periods
  annotate("rect",
           xmin = as.Date("2020-02-03", "%Y-%m-%d"), 
           xmax = as.Date("2020-02-08", "%Y-%m-%d"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  annotate("rect",
           xmin = as.Date("2020-02-15 00:00:00", "%Y-%m-%d"), 
           xmax = as.Date("2020-02-22 00:00:00", "%Y-%m-%d"), 
           ymin = -Inf, 
           ymax = Inf, fill = lightO, alpha = 0.2) +
  # change text size
  theme(text = element_text(size = txt_sz)) +
  ggtitle("(c)") -> tissueLFig
```


# Make a tissue loss model that includes temperature

Before doing any analyses, we want to remove observations from February 4th because that represents tissue loss since the first (multiple days), which is not comparable to the rest. We also want to attach temperature observations to our tissue loss data and remove one influential observation (row 539) found using Cook's distance

```{r}
# remove the 4th
tissueLoss %>% 
  filter(Date != as.Date("2020-02-04")) %>% 
  # update this for the first day of the experiment (no tissue loss)
  mutate(Date = case_when(
    Date == as.Date("2020-01-31") ~ as.Date("2020-02-01"),
    TRUE ~ Date)) %>% 
  left_join(tempMetrics, key = Date) -> tissueLoss4

# we also want to remove the "influential observation" (row 539 diagnosed using code below)
tissueLoss4.f <- tissueLoss4[-539,]
```

## Use a generalized linear model with a binomial family

Because of the large number of zeros in the dataset, we'll use a binomial response variable (0 for no tissue loss, 1 for tissue loss)

```{r}
# make a column for y/n tissue loss
tissueLoss4.f$TissueBin <- ifelse(tissueLoss4.f$Perc_tissue_loss > 0.0, 1, 0)

# make a model for the zeros
m1 <- glm(TissueBin ~ Crab_treatment*Algae_treatment*Wounding_treatment*Mean_C_4, 
          data = tissueLoss4.f, 
          family = binomial(link = logit))


step.bin <- step(m1, direction = "both")
  summary(step.bin)
  
```

Make model predictions

```{r}
# make a dataframe to store predictions in
pred <- expand.grid(Mean_C_4 = seq(min(tissueLoss4.f$Mean_C_4), max(tissueLoss4.f$Mean_C_4), by = 0.05), 
                    Crab_treatment = c("Y", "N"), 
                    Algae_treatment = c("Y", "N"), 
                    Wounding_treatment = c("Y", "N"))

# predict probability of ANY tissue loss
pred$PredProb <- predict(step.bin, pred, type = "response") # response gives the predicted probabilities 

```

### Plot predictions

```{r}
# make labels nice
crab.labs <- c("Crab", "No crab")
names(crab.labs) <- c("Y", "N")


pred %>% 
  # use predicted data
  ggplot(aes(x = Mean_C_4, y = PredProb, color = Algae_treatment, linetype = Wounding_treatment)) +
  geom_line() +
  scale_linetype_manual(values=c("dashed", "solid"),
                        name = "Wounding") +
  # add in actual data
  geom_point(data = tissueLoss4.f, 
             aes(x = Mean_C_4, y = TissueBin, color = Algae_treatment), 
             alpha = 0.2) +
  facet_grid(.~Crab_treatment, labeller = labeller(Crab_treatment = crab.labs)) + # facet by crabs
  ylab("Predicted probability of losing tissue") +
  xlab("Average 4-day water temperature (°C)") +
  scale_color_manual(values = c(forGreen, darkO),
                     name = "Algae") +
  theme_classic() +
  # change text size
  theme(text = element_text(size = txt_sz)) +
  ggtitle("(d)") -> modelfig

```


**Observations from the plot**
See that: 
- Temperature generally increases the probability of losing tissue
- Having algal contact increases the probability of losing tissue
- Wounding increases tissue loss without a crab, but decreases tissue loss with a crab (like survival results)
- The effect of temperature (slope) is less when there is a crab present and when there is no algae present (looks about parallel with no algae + crab)
- Temperature had the largest effect on tissue loss when there was no crab, algae, and wounding


# Check assumptions

## Linearity 

Need to see whether there's linearity using this tutorial: http://www.sthda.com/english/articles/36-classification-methods-essentials/148-logistic-regression-assumptions-and-diagnostics-in-r/

```{r}
# make predictions 
probabilities <- predict(step.bin, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")

# Select only numeric predictors
mydata <- tissueLoss4.f %>%
  dplyr::select(Mean_C_4)  

predictors <- colnames(mydata)

# Bind the logit and tidy the data for plotting
mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

# plot
ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "loess") + 
  theme_bw() + 
  facet_wrap(~predictors, scales = "free_y")
```

This generally looks linear to me, although it's a little weird because of the repeated temperature measures, I think

## Outliers

```{r}
# look for outliers
plot(step.bin, which = 4, id.n = 3)

# Extract model results
model.data <- augment(step.bin) %>% 
  mutate(index = 1:n()) 

model.data %>% top_n(3, .cooksd)


ggplot(model.data, aes(index, .std.resid)) + 
  geom_point(aes(color = TissueBin), alpha = .5) +
  theme_bw()

# look for influential points
model.data %>% 
  filter(abs(.std.resid) > 3) # this shows we're removed all "influential" observations (just one)
```


# Combine figures 

To save these figures as a PDF in the figures folder, remove the pound signs before the `pdf()` and `dev.off()`

```{r}
# pdf(file = here("figures/tissueLTempseries.pdf"), width = 9.5, height = 11)

(tempTSFig + meanTSFig) / (tissueLFig) / (modelfig) 

# dev.off()
```


# Try a mixed model

```{r}
require(lme4)
# require(effects) # for interactions
require(boot) # for inv.logit

# make a column for y/n tissue loss
tissueLoss4.f$TissueBin <- ifelse(tissueLoss4.f$Perc_tissue_loss > 0.0, 1, 0)

# make a mixed model for the zeros
m1 <- glmer(TissueBin ~ Crab_treatment*Algae_treatment*Wounding_treatment*scale(Mean_C_4) + (1|Coral_ID), 
          data = tissueLoss4.f, 
          family = "binomial",
          control=glmerControl(optimizer = "bobyqa", 
                               optCtrl = list(maxfun=2e5))) # this last line just helps it fit 

summary(m1)

# SKIPPING STEPWISE SELECTION--use full model
```


## Check assumptions

### Linearity 

Need to see whether there's linearity using this tutorial: http://www.sthda.com/english/articles/36-classification-methods-essentials/148-logistic-regression-assumptions-and-diagnostics-in-r/

```{r}
# make predictions 
probabilities <- predict(m1, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")

# Select only numeric predictors
mydata <- tissueLoss4.f %>%
  dplyr::select(Mean_C_4)  

predictors <- colnames(mydata)

# Bind the logit and tidy the data for plotting
mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

# plot
ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "loess") + 
  theme_bw() + 
  facet_wrap(~predictors, scales = "free_y")
```

This generally looks linear to me, although it's a little weird because of the repeated temperature measures, I think

### Outliers

```{r}

# Extract model results
model.data <- augment(m1) %>% 
  mutate(index = 1:n()) 

model.data %>% top_n(3, .cooksd)


ggplot(model.data, aes(index, .std.resid)) + 
  geom_point(aes(color = TissueBin), alpha = .5) +
  theme_bw()

# look for influential points
model.data %>% 
  filter(abs(.std.resid) > 3) # this shows there are no "influential" observations 
```



### Plot predictions

```{r}
# make labels nice
crab.labs <- c("Crab", "No crab")
names(crab.labs) <- c("Y", "N")



# make a dataframe to store predictions in
pred <- expand.grid(Mean_C_4 = seq(min(tissueLoss4.f$Mean_C_4), max(tissueLoss4.f$Mean_C_4), by = 0.05), 
                    Crab_treatment = c("Y", "N"), 
                    Algae_treatment = c("Y", "N"), 
                    Wounding_treatment = c("Y", "N"),
                    Coral_ID = 1:80)

# generate predictions
pred$PredProb <- predict(m1, pred, type = "response")

# get the average across corals
pred %>% 
  group_by(Crab_treatment, Algae_treatment, Wounding_treatment, Mean_C_4) %>% 
  summarize(Mean_prob = mean(PredProb), SE = sd(PredProb)/sqrt(n())) -> pred_avg


# plot
  
pred_avg %>% 
  # use predicted data
  ggplot(aes(x = Mean_C_4, y = Mean_prob, color = Algae_treatment, linetype = Wounding_treatment)) +
  geom_line() +
  scale_linetype_manual(values=c("dashed", "solid"),
                        name = "Wounding") +
  # add in actual data
  geom_point(data = tissueLoss4.f, 
             aes(x = Mean_C_4, y = TissueBin, color = Algae_treatment), 
             alpha = 0.2) +
  facet_grid(.~Crab_treatment, labeller = labeller(Crab_treatment = crab.labs)) + # facet by crabs
  ylab("Predicted probability of losing tissue") +
  xlab("Average 4-day water temperature (°C)") +
  scale_color_manual(values = c(forGreen, darkO),
                     name = "Algae") +
  theme_classic() +
  # change text size
  theme(text = element_text(size = txt_sz)) +
  ggtitle("(d)") #-> modelfig

```


## Plot on log odds scale

```{r}
# make a dataframe to store predictions in
predLO <- expand.grid(Mean_C_4 = seq(min(tissueLoss4.f$Mean_C_4), max(tissueLoss4.f$Mean_C_4), by = 0.05), 
                    Crab_treatment = c("Y", "N"), 
                    Algae_treatment = c("Y", "N"), 
                    Wounding_treatment = c("Y", "N"),
                    Coral_ID = 1:80)

# generate predictions
predLO$PredProb <- predict(m1, predLO)

# get the average across corals
predLO %>% 
  group_by(Crab_treatment, Algae_treatment, Wounding_treatment, Mean_C_4) %>% 
  summarize(Mean_prob = mean(PredProb), SE = sd(PredProb)/sqrt(n())) -> pred_avgLO


# plot
  
pred_avgLO %>% 
  # use predicted data
  ggplot(aes(x = Mean_C_4, y = Mean_prob, color = Algae_treatment, linetype = Wounding_treatment)) +
  geom_line() +
  scale_linetype_manual(values=c("dashed", "solid"),
                        name = "Wounding") +
  # add in actual data
  #geom_point(data = tissueLoss4.f, 
  #           aes(x = Mean_C_4, y = TissueBin, color = Algae_treatment), 
   #          alpha = 0.2) +
  facet_grid(.~Crab_treatment, labeller = labeller(Crab_treatment = crab.labs)) + # facet by crabs
  ylab("Log odds of losing tissue") +
  xlab("Average 4-day water temperature (°C)") +
  scale_color_manual(values = c(forGreen, darkO),
                     name = "Algae") +
  theme_classic() +
  # change text size
  theme(text = element_text(size = txt_sz)) +
  ggtitle("(d)") #-> modelfig

```

# Now try to make an interactions plot

```{r}
# get fixed effects 
intercept <- as.numeric(fixef(m1)[1]) # intercept
C <- as.numeric(fixef(m1)[2]) # crab
A <- as.numeric(fixef(m1)[3]) # algae
W <- as.numeric(fixef(m1)[4]) # wounding
Temp <- as.numeric(fixef(m1)[5]) # temperature (scaled)
CA <- as.numeric(fixef(m1)[6]) # crab:algae
CW <- as.numeric(fixef(m1)[7]) # crab:wounding
AW <- as.numeric(fixef(m1)[8]) # algae:wounding
CTemp <- as.numeric(fixef(m1)[9]) # crab:temp
ATemp <- as.numeric(fixef(m1)[10]) # algae:temp
WTemp <- as.numeric(fixef(m1)[11]) # wounding:temp
CAW <- as.numeric(fixef(m1)[12]) # crab:algae:wounding
CATemp <- as.numeric(fixef(m1)[13]) # crab:algae:temp
CWTemp <- as.numeric(fixef(m1)[14]) # crab:wounding:temp
AWTemp <- as.numeric(fixef(m1)[15]) # algae:wounding:temp
CAWTemp <- as.numeric(fixef(m1)[16]) # crab:algae:wounding:temp



```

Make the equation and plot over a range of temperature values

```{r}
# get the value of temperatures we want to predict over
temp_range <- unique(scale(tissueLoss4.f$Mean_C_4))

# make a tibble to hold data
int_table <- tibble(
  T_range = temp_range
)

```

Full interaction equation looks like: 

*intercept + CA + CW + AW + CTemp + ATemp + WTemp + CAW + CATemp + CWTemp + AWTemp + CAWTemp*
- Where a term goes away if it's not in the interaction

```{r}
# look at the effects of just the interactions (no fixed effects) to determine synergy/antagonism/etc.

# generate a function that will generate the effect
# this only works if you've specified C/CA/etc. above (could change that)
get_interaction <- function(Crab_p, Algae_p, Wounding_p, Temp_p, Temp_range) {
  # the parameters are all presences ("p") of each treatment
  impact <- # intercept + 
    (CA*Crab_p*Algae_p) + 
    (CW*Crab_p*Wounding_p) + 
    (AW*Algae_p*Wounding_p) + 
    (CTemp*Crab_p*Temp_p)*Temp_range + 
    (ATemp*Algae_p*Temp_p)*Temp_range + 
    (WTemp*Wounding_p*Temp_p)*Temp_range + 
    (CAW*Crab_p*Algae_p*Wounding_p) + 
    (CATemp*Crab_p*Algae_p*Temp_p)*Temp_range + 
    (CWTemp*Crab_p*Wounding_p*Temp_p)*Temp_range + 
    (AWTemp*Algae_p*Wounding_p*Temp_p)*Temp_range + 
    (CAWTemp*Crab_p*Algae_p*Wounding_p*Temp_p)*Temp_range
  #impact_response <- exp(impact) 
  return(impact)
}


# make sure it works by hand for Crab:Algae:Temperature (no wounding)
crabalgT <- (CA + CTemp*temp_range + ATemp*temp_range + CATemp*temp_range) # removed intercept

# make sure they're the same:
(crabalgT) == get_interaction(Crab_p = 1, Algae_p = 1, Temp_p = 1, Wounding_p = 0, Temp_range = temp_range) # nice!

```

**IS IT RIGHT TO JUST TAKE THE INVERSE LOGIT? ASK. Also how to get the temperature back on an easier to understand scale**

```{r}
# make columns for different interactions
int_table %>% 
  mutate(C_A_T = get_interaction(Crab_p = 1, 
                                    Algae_p = 1, 
                                    Temp_p = 1, 
                                    Wounding_p = 0, 
                                    Temp_range = temp_range),
         C_W_T = get_interaction(Crab_p = 1, 
                                    Algae_p = 0, 
                                    Temp_p = 1, 
                                    Wounding_p = 1, 
                                    Temp_range = temp_range),
         A_W_T = get_interaction(Crab_p = 0, 
                                    Algae_p = 1, 
                                    Temp_p = 1, 
                                    Wounding_p = 1, 
                                    Temp_range = temp_range),
         C_A_W = get_interaction(Crab_p = 1, 
                                    Algae_p = 1, 
                                    Temp_p = 0, 
                                    Wounding_p = 1, 
                                    Temp_range = temp_range),
         C_A = get_interaction(Crab_p = 1, 
                                    Algae_p = 1, 
                                    Temp_p = 0, 
                                    Wounding_p = 0, 
                                    Temp_range = temp_range),
         C_W = get_interaction(Crab_p = 1, 
                                    Algae_p = 0, 
                                    Temp_p = 0, 
                                    Wounding_p = 1, 
                                    Temp_range = temp_range),
         A_W = get_interaction(Crab_p = 0, 
                                    Algae_p = 1, 
                                    Temp_p = 0, 
                                    Wounding_p = 1, 
                                    Temp_range = temp_range),
         C_T = get_interaction(Crab_p = 1, 
                                    Algae_p = 0, 
                                    Temp_p = 1, 
                                    Wounding_p = 0, 
                                    Temp_range = temp_range),
         A_T = get_interaction(Crab_p = 0, 
                                    Algae_p = 1, 
                                    Temp_p = 1, 
                                    Wounding_p = 0, 
                                    Temp_range = temp_range),
         W_T = get_interaction(Crab_p = 0, 
                                    Algae_p = 0, 
                                    Temp_p = 1, 
                                    Wounding_p = 1, 
                                    Temp_range = temp_range),
         C_A_W_T = get_interaction(Crab_p = 1, 
                                    Algae_p = 1, 
                                    Temp_p = 1, 
                                    Wounding_p = 1, 
                                    Temp_range = temp_range)) -> int_effects
```


## Plot it

Change it into long format (easier to plot)

```{r}
int_effects %>% 
  pivot_longer(cols = c(2:length(int_effects)),
               names_to = "Interactions",
               values_to = "Log_odds") %>% 
  # add columns to separate these out
  mutate(Crab = case_when(str_detect(Interactions, pattern = "C") ~ "Y", TRUE ~ "N"),
         Algae = case_when(str_detect(Interactions, pattern = "A") ~ "Y", TRUE ~ "N"),
         Wounding = case_when(str_detect(Interactions, pattern = "W") ~ "Y", TRUE ~ "N"),
         Temperature = case_when(str_detect(Interactions, pattern = "T") ~ "Y", TRUE ~ "N")) -> int_plot
```


From the internet: An odds ratio of 1.46 means Smoking multiplies by 1.46 the probability of having heart disease compared to non-smokers. If β = – 0.38, then eβ = 0.68 and the interpretation becomes: smoking is associated with a 32% (1 – 0.68 = 0.32) reduction in the relative risk of heart disease.

Log odds (what we plot below) I believe is neutral at 0, then is less likely in negatives and more likely in positives

```{r}
int_plot %>% 
  filter(Temperature == "Y") %>% 
  ggplot(aes(x = T_range, y = Log_odds, color = Algae, linetype = Wounding)) +
  scale_color_manual(values = c(darkO, forGreen),
                     name = "Algae") + 
  geom_line() +
  geom_hline(yintercept = 0) +
  scale_linetype_manual(values=c("solid", "dashed"),
                        name = "Wounding") +
  ylab("Marginal change in log odds of tissue loss") +
  xlab("Temperature (scaled)") +
  theme_bw() +
  facet_wrap(.~Crab, labeller = label_both) 
  
```



How do we get standard errors? Try for no temperature interactions

```{r}
emmeans(m1, ~ Crab_treatment * Algae_treatment * Wounding_treatment) %>% 
  as.data.frame() %>% 
  rename(Crab = Crab_treatment,
         Algae = Algae_treatment,
         Wounding = Wounding_treatment) -> noTse


# can we join it then plot?
int_plot %>% 
  filter(Temperature == "N") %>% 
  inner_join(noTse, by = c("Crab", "Algae", "Wounding")) %>% 
  ggplot(aes(x = Interactions, y = Log_odds, color = Crab, linetype = Wounding)) +
  scale_color_manual(values = c(vibRed, skyB),
                     name = "Crab") +
  geom_point(aes(x = Interactions, y = Log_odds)) +
  geom_errorbar(aes(ymin = Log_odds-(SE*qnorm(0.975)), # 95% confidence intervals
                    ymax = Log_odds+(SE*qnorm(0.975))), 
                width=.2,
                 position=position_dodge(0.05)) +
  ylab("Marginal change in log odds of tissue loss") +
  xlab("") +
  geom_hline(yintercept = 0) +
  
  scale_x_discrete(breaks=c("A_W","C_A","C_A_W", "C_W"),
        labels=c("Algae:Wound", "Algae:Crab", "Algae:Crab:Wound", "Crab:Wound")) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 35, hjust=  1)) 

```

Or do I need to do it like suggested here: https://cran.r-project.org/web/packages/lme4/vignettes/lmer.pdf ?

In which case it would look like:

```{r}
confint(m1, method = "Wald")

as.data.frame(confint(m1, method = "Wald")) %>% 
  rownames_to_column(var = "Term") %>% 
  # get rid of this row
  filter(Term != ".sig01") %>% 
  # add columns to separate these out
  mutate(Crab = case_when(str_detect(Term, pattern = "Crab") ~ "Y", TRUE ~ "N"),
         Algae = case_when(str_detect(Term, pattern = "Algae") ~ "Y", TRUE ~ "N"),
         Wounding = case_when(str_detect(Term, pattern = "Wounding") ~ "Y", TRUE ~ "N"),
         Temperature = case_when(str_detect(Term, pattern = "Mean_C_4") ~ "Y", TRUE ~ "N")) %>% 
  filter(Temperature != "Y") -> waldplot
```

Join then plot

```{r}
# can we join it then plot?
int_plot %>% 
  filter(Temperature == "N") %>% 
  inner_join(waldplot, by = c("Crab", "Algae", "Wounding", "Temperature")) %>% 
  ggplot(aes(x = Interactions, y = Log_odds, color = Crab, linetype = Wounding)) +
  scale_color_manual(values = c(vibRed, skyB),
                     name = "Crab") +
  geom_point(aes(x = Interactions, y = Log_odds)) +
  #geom_errorbar(aes(ymin = `2.5 %`, # 95% confidence intervals
   #                 ymax = `97.5 %`, 
   #             width=.2)) +
  ylab("Marginal change in log odds of tissue loss") +
  xlab("") +
  geom_hline(yintercept = 0) +
  
  scale_x_discrete(breaks=c("A_W","C_A","C_A_W", "C_W"),
        labels=c("Algae:Wound", "Algae:Crab", "Algae:Crab:Wound", "Crab:Wound")) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 35, hjust=  1)) 

```


Hmmm I think yes the error bars are not correct. Need to figure out how to get those 

## Error bars

First get covariance matrix

```{r}
vcov.m1 <- vcov(m1)
```

Code below is probably not useful come back later

```{r}
# varCA <- vcov.m1["Crab_treatmentY:Algae_treatmentY", "Crab_treatmentY:Algae_treatmentY"]
# varCW <- vcov.m1["Crab_treatmentY:Wounding_treatmentY", "Crab_treatmentY:Wounding_treatmentY"]
```


Then zero out the terms we're not interested in

```{r}
vcov.m1[4:16,] = 0 
vcov.m1[,4:16] = 0

```

Get coefficients

```{r}
coeffic <- fixef(m1)
coeffic_mat<- coeffic%*%t(coeffic)
coeffic_mat[4:16,]=0
coeffic_mat[,4:16]=0


var.fe <- sum(coeffic_mat * vcov.m1)
```

```{r}
# by hand:
var.fe2 <- as.numeric(coeffic[1])^2*vcov.m1[1,1] + as.numeric(coeffic[2])^2*vcov.m1[2,2] + as.numeric(coeffic[3])^2*vcov.m1[3,3] + 2*coeffic[1]*coeffic[2]*vcov.m1[1,2] + 2*coeffic[2]*coeffic[3]*vcov.m1[2,3] + 2*coeffic[1]*coeffic[3]*vcov.m1[1,3]


```

## Make it a function

```{r}
get_variance <- function(coeff_vector, vcov_matrix, term_list) { # create a function to get the variance of a linear combination of some of these terms
  # coeff_vector = a vector of model coefficients in the same order as cov_matrix, but with 1's, 0's or temperature ranges. Can get from fixef(your_model)
  # vcov_matrix = a variance covariance matrix from the model. Can get from vcov(model)
  # term_list = a list of coefficients from your model that you want to include in the calculation
  
  # first, make a vector with the correct dimensions/labels, but with zeros to use as a mask
  mask <- coeff_vector
  mask[] = 0
  # then, populate items we care about (on the term_list) with 1's
  for (term in 1:length(term_list)) 
  { 
    mask[(term_list[term])] = 1 # set item to 1
  }
  
  # then make coefficient vector zeros where needed
  coeff_vector <- mask*coeff_vector
  
  # then make a coefficient matrix
  coeffic_mat <- coeff_vector %*% t(coeff_vector)
  
  # then sum to get the variance
  var <- sum(coeffic_mat*vcov_matrix)
  return(var)
  
}
```

Test

```{r}
# by function:
get_variance(coeff_vector = fixef(m1), 
             vcov_matrix = vcov(m1), 
             term_list = c("Wounding_treatmentY", "Crab_treatmentY", "Algae_treatmentY"))

# by hand:
vcov.m1 <- vcov(m1)

as.numeric(coeffic[4])^2*vcov.m1[4,4] + as.numeric(coeffic[2])^2*vcov.m1[2,2] + as.numeric(coeffic[3])^2*vcov.m1[3,3] + 2*coeffic[4]*coeffic[2]*vcov.m1[4,2] + 2*coeffic[2]*coeffic[3]*vcov.m1[2,3] + 2*coeffic[4]*coeffic[3]*vcov.m1[4,3] # nice
```


## Function again

```{r}
get_variance <- function(coeff_vector, vcov_matrix) { # create a function to get the variance of a linear combination of some of these terms
  # coeff_vector = a vector of model coefficients in the same order as cov_matrix, but with 1's, 0's or temperature ranges. Can get from fixef(your_model) then alter by doing variable[]=0, variable[variable of interest]=1, variable[variable of interest]= temp:range
  # vcov_matrix = a variance covariance matrix from the model. Can get from vcov(model)
  # term_list = a list of coefficients from your model that you want to include in the calculation
  
  # make a coefficient matrix
  coeffic_mat <- coeff_vector %*% t(coeff_vector)
  
  # then sum to get the variance
  var <- sum(coeffic_mat*vcov_matrix)
  return(var)
  
}
```


Try

```{r}
coeff_vector <- fixef(m1)
coeff_vector[]=0
coeff_vector["Crab_treatmentY"]=1
coeff_vector["Wounding_treatmentY"]=1
coeff_vector["scale(Mean_C_4)"] = [[seq(from = -2, to = 2, length.out = 24)]]


```


```{r}
get_interaction <- function(Crab_p, Algae_p, Wounding_p, Temp_p, Temp_range) {
  # the parameters are all presences ("p") of each treatment
  # temp_range is a vector of temperature ranges you want variances for 
  variance <-
    (Crab_p*Algae_p) + 
    (Crab_p*Wounding_p) + 
    (Algae_p*Wounding_p) + 
    (Crab_p*Temp_p)*Temp_range + 
    (Algae_p*Temp_p)*Temp_range + 
    (Wounding_p*Temp_p)*Temp_range + 
    (Crab_p*Algae_p*Wounding_p) + 
    (Crab_p*Algae_p*Temp_p)*Temp_range + 
    (Crab_p*Wounding_p*Temp_p)*Temp_range + 
    (Algae_p*Wounding_p*Temp_p)*Temp_range + 
    (Crab_p*Algae_p*Wounding_p*Temp_p)*Temp_range
  #impact_response <- exp(impact) 
  return(variance)
}
```



# Add errors?

Need sample sizes

```{r}



```

## Try function again

```{r}
get_variance <- function(Crab_p, Algae_p, Wounding_p, Temp_p, Temp_range, vcov_matrix) { # create a function to get the variance of a linear combination of some of these terms
  # the parameters are all presences ("p") of each treatment
  # temp_range is a vector of temperature ranges you want variances for 
  # vcov_matrix = a variance covariance matrix from the model. Can get from vcov(model)
  
  
  # coeff_matrix = this is a matrix of 11 columns (or # of terms you have) by 50 rows (or however many temperature values you want to predict for). Terms included should be "1" down the column and terms excluded should be "0". Terms with temperature should use the temperature range
  coeff_matrix <- matrix(0, nrow = length(Temp_range), ncol = dim(vcov_matrix)[1])
  colnames(coeff_matrix) <- colnames(vcov_matrix) # add names back
  #coeff_matrix[] <- 1 # sets all to 1
  
  # populate values needed for temperature
  #for (col in 1:length(colnames(coeff_matrix))) {
  #  vect <- case_when(str_detect(colnames(coeff_matrix)[col], pattern = "Mean_C_4") ~ Temp_range,
  #                  TRUE ~ rep(1, length(Temp_range)))
  #  coeff_matrix[,col] <- vect
  #}
  
  # put zeros where needed
  # for main effects (just looking at interaction terms)
  coeff_matrix[,1:5]=0
  # for other irrelevant terms
  coeff_matrix[,"Crab_treatmentY:Algae_treatmentY"] = Crab_p*Algae_p
  coeff_matrix[,"Crab_treatmentY:Wounding_treatmentY"] = Crab_p*Wounding_p
  coeff_matrix[,"Algae_treatmentY:Wounding_treatmentY"] = Algae_p*Wounding_p
  coeff_matrix[,"Crab_treatmentY:scale(Mean_C_4)"] = Crab_p*Temp_range
  coeff_matrix[,"Algae_treatmentY:scale(Mean_C_4)"] = Algae_p*Temp_range
  coeff_matrix[,"Wounding_treatmentY:scale(Mean_C_4)"] = Wounding_p*Temp_range
  coeff_matrix[,"Crab_treatmentY:Algae_treatmentY:Wounding_treatmentY"] = Crab_p*Algae_p*Wounding_p
  coeff_matrix[,"Crab_treatmentY:Algae_treatmentY:scale(Mean_C_4)"] = Crab_p*Algae_p*Temp_range
  coeff_matrix[,"Crab_treatmentY:Wounding_treatmentY:scale(Mean_C_4)"] = Crab_p*Wounding_p*Temp_range
  coeff_matrix[,"Algae_treatmentY:Wounding_treatmentY:scale(Mean_C_4)"] = Algae_p*Wounding_p*Temp_range
  coeff_matrix[,"Crab_treatmentY:Algae_treatmentY:Wounding_treatmentY:scale(Mean_C_4)"] = Crab_p*Algae_p*Wounding_p*Temp_range
  
  
  # loop through to get the variance
  variance_sum <- rep(0, times = length(Temp_range)) # initialize
  # loop
  for (i in 1:dim(vcov_matrix)[1]) {
    for (j in 1:dim(vcov_matrix)[2]) {
      variance_sum = variance_sum + coeff_matrix[,i]*coeff_matrix[,j]*vcov_matrix[i,j]
    }
  }
  
  return(variance_sum)
  
}
```


Test it

```{r}
get_variance(Crab_p = 1, Algae_p = 1, Wounding_p = 0, Temp_p = 1, Temp_range = seq(-1.5, 1.5, length.out = 40), vcov_matrix = vcov(m1))
```


Compare to by hand

```{r}
vcov.m1 <- vcov(m1)
Temp_range <- seq(-1.5, 1.5, length.out = 40)

vcov.m1["Crab_treatmentY:Algae_treatmentY", "Crab_treatmentY:Algae_treatmentY"] + vcov.m1["Crab_treatmentY:scale(Mean_C_4)", "Crab_treatmentY:scale(Mean_C_4)"]*Temp_range^2 +
  vcov.m1["Algae_treatmentY:scale(Mean_C_4)", "Algae_treatmentY:scale(Mean_C_4)"]*Temp_range^2 +
  vcov.m1["Crab_treatmentY:Algae_treatmentY:scale(Mean_C_4)", "Crab_treatmentY:Algae_treatmentY:scale(Mean_C_4)"]*Temp_range^2 +
  vcov.m1["Crab_treatmentY:Algae_treatmentY", "Crab_treatmentY:scale(Mean_C_4)"]*2*Temp_range +
  vcov.m1["Crab_treatmentY:Algae_treatmentY", "Algae_treatmentY:scale(Mean_C_4)"]*2*Temp_range +
  vcov.m1["Crab_treatmentY:scale(Mean_C_4)", "Algae_treatmentY:scale(Mean_C_4)"]*2*Temp_range*Temp_range +
  vcov.m1["Crab_treatmentY:Algae_treatmentY:scale(Mean_C_4)", "Crab_treatmentY:scale(Mean_C_4)"]*2*Temp_range*Temp_range +
  vcov.m1["Crab_treatmentY:Algae_treatmentY", "Crab_treatmentY:Algae_treatmentY:scale(Mean_C_4)"]*2*Temp_range +
  vcov.m1["Crab_treatmentY:Algae_treatmentY:scale(Mean_C_4)", "Algae_treatmentY:scale(Mean_C_4)"]*2*Temp_range*Temp_range
  
  
  
```



## Try to plot?

Get variances for the lines. Should be sqrt(variance)*1.96 for 95% CIs. Add this to the int_plot data frame

```{r}
int_plot %>% 
  # first change to 0's/1's for the input to the function
  mutate(Crab = case_when(Crab == "Y" ~ 1,
                          Crab == "N" ~ 0)) %>% 
  mutate(Wounding = case_when(Wounding == "Y" ~ 1,
                              Wounding == "N" ~ 0)) %>% 
  mutate(Algae = case_when(Algae == "Y" ~ 1,
                           Algae == "N" ~ 0)) %>% 
  mutate(Temperature = case_when(Temperature == "Y" ~ 1,
                                 Temperature == "N" ~ 0)) %>% 
  # call our function
  mutate(Variance = get_variance(Crab_p = Crab, 
                                 Algae_p = Algae, 
                                 Wounding_p = Wounding, 
                                 Temp_p = Temperature, 
                                 Temp_range = T_range,
                                 vcov_matrix = vcov(m1))) %>% 
  mutate(CI95 = 1.96*sqrt(Variance)) -> int_variance

# clean up the dataframe by switching factors back to factors
int_variance %>% 
  select(-Crab, -Wounding, -Algae, -Temperature) %>% 
  left_join(int_plot, by = c("T_range", "Interactions", "Log_odds")) -> int_variance_fact
```


### Plot temp graph

```{r}

int_variance_fact %>% 
  filter(Temperature == "Y") %>% 
  ggplot(aes(x = T_range, y = Log_odds, color = Wounding, linetype = Wounding)) +
  scale_color_manual(values = c(lightO, skyB),
                     name = "Wounding") + 
  geom_line() +
  geom_hline(yintercept = 0) +
  scale_linetype_manual(values=c("solid", "dashed"),
                        name = "Wounding") +
  
  geom_ribbon(aes(ymin=Log_odds-CI95, ymax=Log_odds+CI95, fill = Wounding), alpha = 0.5) +
  scale_fill_manual(values = c(lightO, skyB),
                     name = "Wounding") +
  
  ylab("Marginal change in log odds of tissue loss") +
  xlab("Temperature (scaled)") +
  theme_bw() +
  facet_grid(Crab ~Algae, labeller = label_both) 
  
```

What can we say about that? That it looks like 
